### 2016-03-21 README.Rmd
updated README

---
title: "MacLeish"
output:
  html_document:
    keep_md: true
---

[![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)

The Ada and Archibald MacLeish Field Station is a 240-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.  More information can be found at (http://www.smith.edu/ceeds/macleish.php)

This R package allows you to download and process weather data (as a time series) using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.

## To install

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("beanumber/etl")
devtools::install_github("beanumber/macleish")
```

### 2016-03-21 README.Rmd
updated README

@@
 ```
+
+## Use 2015 weather data
+
+Weather data from 2015 is available immediately from two both the `Whately` and `Orchard` weather stations.
+
+```{r, message=FALSE}
+library(macleish)
+glimpse(whately_2015)
+glimpse(orchard_2015)
+```
+
+## Live weather data
+
+Weather readings are logged every 10 minutes.
+Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](http://www.github.com/beanumber/etl) framework.
+Please see the documentation for that package for more information about how this works.
+
+```{r, message=FALSE}
+macleish <- etl("macleish")
+macleish %>%
+  etl_update()
+```
+
+```{r}
+whately <- macleish %>%
+  tbl("whately")
+whately %>%
+  mutate(the_year = strftime('%Y', when)) %>%
+  group_by(the_year) %>%
+  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
+orchard <- macleish %>%
+  tbl("orchard")
+orchard %>%
+  mutate(the_year = strftime('%Y', when)) %>%
+  group_by(the_year) %>%
+  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
+```
+
+```{r, fig.width = 7, fig.height = 5, message=FALSE}
+daily <- whately %>%
+  mutate(the_date = date(when)) %>%
+  group_by(the_date) %>%
+  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
+  collect()
+library(ggplot2)
+ggplot(data = daily, aes(x = as.Date(the_date), y = avgTemp)) +
+  geom_point() + geom_smooth()
+```
+
+## Maps
+
+Spatial data is available through the `macleish_layers` data object.
+
+```{r}
+class(macleish_layers)
+names(macleish_layers)
+```
+
+```{r, fig.width=7, fig.height=7, message=FALSE}
+library(leaflet)
+leaflet() %>%
+  addTiles() %>%
+  addPolygons(data = macleish_layers[["buildings"]], 
+              weight = 1, popup = ~ Feature) %>%
+  addPolylines(data = macleish_layers[["trails"]], 
+               weight = 1, color = "brown",
+               popup = ~ Name) %>%
+  addPolylines(data = macleish_layers[["streams"]], 
+               weight = 2)
+```

### 2016-03-21 R/data.R
updated spatial data and README

@@ -52,18 +52,17 @@
 #' 
 #' \describe{
 #'  \item{landmarks}{Landmarks}
-#'  \item{vernal_pool}{A vernal pool}
 #'  \item{forests}{Type of dominant tree in individual forests, as 
 #'  noted by Jesse Bellemare}
 #'  \item{streams}{local streams}
 #'  \item{challenge_courses}{Challenge courses on the property}
-#'  \item{macleish_boundary}{boundary of the field station}
 #'  \item{reservoir}{a reservoir}
-#'  \item{property_boundary}{the boundary of the property}
 #'  \item{buildings}{Buildings at MacLeish}
-#'  \item{slopes}{steep slopes}
 #'  \item{wetlands}{Wetland areas}
 #'  \item{trails}{Hiking trails}
+#'  \item{slopes}{steep slopes}
+#'  \item{schools}{Schools in Massachusetts}
+#'  \item{boundary}{the property boundary}
 #' }
 #' 
 #' @examples 

### 2016-03-21 data-raw/macleish.R

@@ -27,21 +27,21 @@ list.files(dsn)
 ogrListLayers(dsn)
 ogrInfo(dsn, layer = "Trails")
 
-layers <- c("Key Landmarks", "VernalPool", "VegType_2009_20101112", "Streams", 
-            "ChallengeCourse_Elements", "MacLeishBoundary", "Reservoir", 
-            "Property Boundary", "Buildings", "Steep Slopes", "Wetlands",
-            "Trails")
+layers <- c("Key Landmarks", "VegType_2009_20101112", "Streams", 
+            "ChallengeCourse_Elements", "Reservoir", 
+            "Buildings", "Wetlands",
+            "Trails", "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary")
 macleish_layers <- lapply(layers, readOGR, dsn = dsn)
 
-names(macleish_layers) <- c("landmarks", "vernal_pool", "forests", "streams",
-                            "challenge_courses", "macleish_boundary", "reservoir", 
-                            "property_boundary", "buildings", "slopes", "wetlands",
-                            "trails")
+names(macleish_layers) <- c("landmarks", "forests", "streams",
+                            "challenge_courses", "reservoir", 
+                            "buildings", "wetlands",
+                            "trails", "slopes", "schools", "boundary")
 
 lapply(macleish_layers, proj4string)
 
-# fix the Steep Slopes projection string
-proj4string(macleish_layers[[10]]) <- proj4string(macleish_layers[[1]])
+# fix the projection string
+# proj4string(macleish_layers[[10]]) <- proj4string(macleish_layers[[1]])
 
 macleish_layers <- lapply(macleish_layers, spTransform, CRSobj = CRS("+init=epsg:4326"))
 

### 2016-03-21 R/etl_extract.R
updated Rbuildignore

@@ -9,6 +9,7 @@
 #' macleish <- etl("macleish")
 #' str(macleish)
 #' 
+#' \dontrun{
 #' macleish %>%
 #'   etl_extract() %>%
 #'   etl_transform() %>%
@@ -18,6 +19,7 @@
 #'   
 #' whately %>%
 #'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
+#' }
 
 etl_extract.etl_macleish <- function(obj, ...) {
   url <- "https://scidb.smith.edu/~macleish/"

### 2016-03-25 README.Rmd
fixed type in README
added research plots

@@
 
-The Ada and Archibald MacLeish Field Station is a 240-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
+The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
 Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.
@@
 
-Weather data from 2015 is available immediately from two both the `Whately` and `Orchard` weather stations.
+Weather data from 2015 is available immediately from both the `Whately` and `Orchard` weather stations.
 
@@
   addTiles() %>%
+  addPolygons(data = macleish_layers[["boundary"]], 
+              weight = 1, fillOpacity = 0.1) %>%
   addPolygons(data = macleish_layers[["buildings"]], 

### 2016-03-25 R/data.R

@@ -63,6 +63,8 @@
 #'  \item{slopes}{steep slopes}
 #'  \item{schools}{Schools in Massachusetts}
 #'  \item{boundary}{the property boundary}
+#'  \item{research}{research plots}
+#'  \item{soil}{soil deposits used by Amy Rhodes}
 #' }
 #' 
 #' @examples 

### 2016-03-25 R/etl_extract.R

@@ -16,9 +16,18 @@
 #'   etl_load()
 #' whately <- macleish %>%
 #'   tbl("whately") 
+#' orchard <- macleish %>%
+#'   tbl("orchard") 
 #'   
 #' whately %>%
 #'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
+#' orchard %>%
+#'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
+#' 
+#' # show the most recent data -- should be within the past hour
+#' whately %>%
+#'   collect() %>%
+#'   tail()
 #' }
 
 etl_extract.etl_macleish <- function(obj, ...) {

### 2016-03-25 data-raw/macleish.R
docs and data-raw

@@ -30,13 +30,15 @@ ogrInfo(dsn, layer = "Trails")
 layers <- c("Key Landmarks", "VegType_2009_20101112", "Streams", 
             "ChallengeCourse_Elements", "Reservoir", 
             "Buildings", "Wetlands",
-            "Trails", "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary")
+            "Trails", "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary",
+            "Research_Poly", "Rhodes_soil")
 macleish_layers <- lapply(layers, readOGR, dsn = dsn)
 
 names(macleish_layers) <- c("landmarks", "forests", "streams",
                             "challenge_courses", "reservoir", 
                             "buildings", "wetlands",
-                            "trails", "slopes", "schools", "boundary")
+                            "trails", "slopes", "schools", "boundary", 
+                            "research", "soil")
 
 lapply(macleish_layers, proj4string)
 

### 2016-03-28 data-raw/macleish.R
updated trails layer

@@ -30,15 +30,15 @@ ogrInfo(dsn, layer = "Trails")
 layers <- c("Key Landmarks", "VegType_2009_20101112", "Streams", 
             "ChallengeCourse_Elements", "Reservoir", 
             "Buildings", "Wetlands",
-            "Trails", "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary",
-            "Research_Poly", "Rhodes_soil")
+            "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary",
+            "Research_Poly", "Rhodes_soil", "Trails_20160328")
 macleish_layers <- lapply(layers, readOGR, dsn = dsn)
 
 names(macleish_layers) <- c("landmarks", "forests", "streams",
                             "challenge_courses", "reservoir", 
                             "buildings", "wetlands",
-                            "trails", "slopes", "schools", "boundary", 
-                            "research", "soil")
+                            "slopes", "schools", "boundary", 
+                            "research", "soil", "trails")
 
 lapply(macleish_layers, proj4string)
 

### 2016-03-30 README.Rmd

@@
 
-The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
+The Ada and Archibald MacLeish Field Station is a 240-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
 Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.

### 2016-03-30 README.Rmd
updated README and added weather station locations

--- 2016-03-25 README.Rmd
@@
 
-```{r, message=FALSE}
+```{r, message=FALSE, eval=FALSE}
 macleish <- etl("macleish")
@@
 
-```{r}
+```{r, eval=FALSE}
 whately <- macleish %>%
@@
 
-```{r, fig.width = 7, fig.height = 5, message=FALSE}
+```{r, eval=FALSE, fig.width = 7, fig.height = 5, message=FALSE}
 daily <- whately %>%
@@
                weight = 1, color = "brown",
-               popup = ~ Name) %>%
+               popup = ~ trl_name) %>%
   addPolylines(data = macleish_layers[["streams"]], 

### 2016-03-30 R/data.R

@@ -5,7 +5,10 @@
 #'
 #' @details The Macleish Field Station is a remote outpost owned by Smith
 #' College and used for field research. There are two weather stations on the 
-#' premises. One is called \code{Whately} and the other is \code{Orchard}.
+#' premises. One is called \code{WhatelyMet} and the other is \code{OrchardMet}.
+#' 
+#' The \code{WhatelyMet} station is located at (42.448470, -72.680553) and
+#' the \code{OrchardMet} station is at (42.449653, -72.680315).
 #' 
 #' Solar radiation is measured in two different ways: see \code{SlrW_Avg}
 #' or the \code{PAR} variables for Photosynthetic Active Radiation.

### 2016-04-06 data-raw/macleish.R
tiny edits to data_raw script

@@ -1,4 +1,4 @@
-
+# Creates 2015 data for Whately and Orchard
 
 macleish <- etl("macleish") %>%
   etl_extract() %>%
@@ -20,6 +20,7 @@ orchard_2015 <- macleish %>%
 save(whately_2015, file = "data/whately_2015.rda", compress = "xz")
 save(orchard_2015, file = "data/orchard_2015.rda", compress = "xz")
 
+# Creates the macleish_layers list
 
 library(rgdal)
 dsn <- path.expand("~/Dropbox/Data for Ben Baumer/")

### 2016-04-06 R/etl_extract.R
added distinct() #8

@@ -60,7 +60,8 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(RH_per_Avg = ~as.numeric(RH_per_Avg)) %>%
     mutate_(Press_mb_Avg = ~as.numeric(Press_mb_Avg)) %>%
     mutate_(SlrW_Avg = ~as.numeric(SlrW_Avg)) %>%
-    mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot))
+    mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
+    distinct()
   write.csv(out, file = paste0(attr(obj, "load_dir"), "/whately.csv"), row.names = FALSE)
   # Orchard
   lcl <- paste0(attr(obj, "raw_dir"), "/OrchardMet_Met_10min.dat")
@@ -77,7 +78,8 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Press_mb_Avg = ~as.numeric(Press_mb_Avg)) %>%
     mutate_(PAR_Den_Avg = ~as.numeric(PAR_Den_Avg)) %>%
     mutate_(PAR_Tot_Avg = ~as.numeric(PAR_Tot_Avg)) %>%
-    mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot))
+    mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
+    distinct()
   write.csv(out, file = paste0(attr(obj, "load_dir"), "/orchard.csv"), row.names = FALSE)
   invisible(obj)
 }

### 2016-04-07 R/etl_extract.R
Implemented readr, and close #12

@@ -23,6 +23,16 @@
 #'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
 #' orchard %>%
 #'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
+#'   
+#' # check data types
+#' whately %>%
+#'   glimpse()
+#' 
+#' # if using SQLite, datetimes will get converted to integers
+#' whately <- whately %>%
+#'   mutate(when_datetime = datetime(when, 'unixepoch'))
+#' whately %>%
+#'   glimpse()
 #' 
 #' # show the most recent data -- should be within the past hour
 #' whately %>%
@@ -86,22 +96,27 @@ etl_transform.etl_macleish <- function(obj, ...) {
 
 #' @rdname etl_extract.etl_macleish
 #' @importFrom DBI dbWriteTable
+#' @importFrom readr read_csv cols col_double
 #' @export
 
 etl_load.etl_macleish <- function(obj, ...) {
   # Whately
-  data <- read.csv(paste0(attr(obj, "load_dir"), "/whately.csv"))
+  data <- readr::read_csv(paste0(attr(obj, "load_dir"), "/whately.csv"), 
+                          col_types = readr::cols(Rain_mm_Tot = readr::col_double()))
   # write the table to the DB
   message("Writing whately data to the database...")
-  if (DBI::dbWriteTable(obj$con, "whately", data, overwrite = TRUE, row.names = FALSE, ...)) {
+  if (DBI::dbWriteTable(obj$con, "whately", as.data.frame(data), 
+                        overwrite = TRUE, row.names = FALSE, ...)) {
     message("Data was successfully written to database.")
     message(DBI::dbListTables(obj$con))
   }
   # Orchard
-  data <- read.csv(paste0(attr(obj, "load_dir"), "/orchard.csv"))
+  data <- readr::read_csv(paste0(attr(obj, "load_dir"), "/orchard.csv"), 
+                   col_types = readr::cols(Rain_mm_Tot = readr::col_double()))
   # write the table to the DB
   message("Writing orchard data to the database...")
-  if (DBI::dbWriteTable(obj$con, "orchard", data, overwrite = TRUE, row.names = FALSE, ...)) {
+  if (DBI::dbWriteTable(obj$con, "orchard", as.data.frame(data), 
+                        overwrite = TRUE, row.names = FALSE, ...)) {
     message("Data was successfully written to database.")
     message(DBI::dbListTables(obj$con))
   }

### 2016-04-07 README.Rmd
moved to GitHub README

@@
 output:
-  html_document:
-    keep_md: true
+  github_document:
+    html_preview: true
 ---
@@
 
-```{r, fig.width=7, fig.height=7, message=FALSE}
+```{r, eval=FALSE, fig.width=7, fig.height=7, message=FALSE}
 library(leaflet)

### 2016-04-07 data-raw/spatial.R
split data_raw scripts and updated weather data

@@ -1,25 +1,3 @@
-# Creates 2015 data for Whately and Orchard
-
-macleish <- etl("macleish") %>%
-  etl_extract() %>%
-  etl_transform() %>%
-  etl_load()
-
-whately_2015 <- macleish %>%
-  tbl("whately") %>%
-  mutate(the_year = strftime('%Y', when)) %>%
-  collect() %>%
-  filter(the_year == 2015)
-
-orchard_2015 <- macleish %>%
-  tbl("orchard") %>%
-  mutate(the_year = strftime('%Y', when)) %>%
-  collect() %>%
-  filter(the_year == 2015)
-
-save(whately_2015, file = "data/whately_2015.rda", compress = "xz")
-save(orchard_2015, file = "data/orchard_2015.rda", compress = "xz")
-
 # Creates the macleish_layers list
 
 library(rgdal)

### 2016-04-07 data-raw/spatial.R
added spatial data; close #14

@@ -1,29 +1,38 @@
 # Creates the macleish_layers list
 
 library(rgdal)
-dsn <- path.expand("~/Dropbox/Data for Ben Baumer/")
+dsn <- path.expand("data-raw/macleish/")
 list.files(dsn)
 ogrListLayers(dsn)
-ogrInfo(dsn, layer = "Trails")
+ogrInfo(dsn, layer = "trails")
 
-layers <- c("Key Landmarks", "VegType_2009_20101112", "Streams", 
-            "ChallengeCourse_Elements", "Reservoir", 
-            "Buildings", "Wetlands",
-            "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary",
-            "Research_Poly", "Rhodes_soil", "Trails_20160328")
+# layers <- c("Key Landmarks", "VegType_2009_20101112", "Streams", 
+            # "ChallengeCourse_Elements", "Reservoir", 
+            # "Buildings", "Wetlands",
+            # "Slope2016", "SCHOOLS_PT", "2016_MacLeish_Boundary",
+            # "Research_Poly", "Rhodes_soil", "Trails_20160328")
+
+layers <- c("landmarks", "forests", "streams",
+  "challenge_courses", 
+  "buildings", "wetlands",
+  "slopes", "boundary", 
+  "research", "soil", "trails")
+
 macleish_layers <- lapply(layers, readOGR, dsn = dsn)
+names(macleish_layers) <- layers
 
-names(macleish_layers) <- c("landmarks", "forests", "streams",
-                            "challenge_courses", "reservoir", 
-                            "buildings", "wetlands",
-                            "slopes", "schools", "boundary", 
-                            "research", "soil", "trails")
+# names(macleish_layers) <- c("landmarks", "forests", "streams",
+#                             "challenge_courses", "reservoir", 
+#                             "buildings", "wetlands",
+#                             "slopes", "schools", "boundary", 
+#                             "research", "soil", "trails")
 
+# check to make sure they are all projected the same
 lapply(macleish_layers, proj4string)
 
 # fix the projection string
 # proj4string(macleish_layers[[10]]) <- proj4string(macleish_layers[[1]])
 
-macleish_layers <- lapply(macleish_layers, spTransform, CRSobj = CRS("+init=epsg:4326"))
+# macleish_layers <- lapply(macleish_layers, spTransform, CRSobj = CRS("+init=epsg:4326"))
 
 save(macleish_layers, file = "data/macleish_layers.rda", compress = "xz")

### 2016-04-10 README.Rmd

@@
 whately %>%
-  mutate(the_year = strftime('%Y', when)) %>%
+  mutate(the_year = strftime('%Y', when, 'unixepoch')) %>%
   group_by(the_year) %>%
@@
 orchard %>%
-  mutate(the_year = strftime('%Y', when)) %>%
+  mutate(the_year = strftime('%Y', when, 'unixepoch')) %>%
   group_by(the_year) %>%
@@
 daily <- whately %>%
-  mutate(the_date = date(when)) %>%
+  mutate(the_date = date(when, 'unixepoch')) %>%
   group_by(the_date) %>%

### 2016-04-25 R/data.R
changed order of variables in documentation

@@ -21,12 +21,11 @@
 #' All variables are averaged over the 10 minute inverval unless otherwise noted.
 #' \describe{
 #'   \item{when}{timestamp for each measurment set.}
-#'   \item{record}{Starting from the first measurements recorded from the year, goes up by 1 every 10 minutes.}
+#'   \item{Temp_C_Avg}{average temperature, in Celsius}
 #'   \item{WSpd_mps}{Wind speed, in  meters per second}
 #'   \item{Wdir_deg}{Wind direction, in degrees}
-#'   \item{Temp_C_Avg}{average temperature, in Celsius}
-#'   \item{Press_mb_Avg}{Atmospheric pressure, in millibars}
 #'   \item{RH_per_Avg}{How much water there is in the air, in millimeters}
+#'   \item{Press_mb_Avg}{Atmospheric pressure, in millibars}
 #'   \item{Rain_mm_Tot}{Total rainfall, in millimeters}
 #'   \item{SlrW_Avg}{Amount of radiation coming from the sun, in Watts/meters^2. Solar measurement for Whatley}
 #'   \item{PAR_Den_Avg}{Measures solar radiation. One of two solar measurements for Orchard}

### 2016-04-26 README.Rmd
cleanup after previous commits

@@
   addPolygons(data = macleish_layers[["buildings"]], 
-              weight = 1, popup = ~ Feature) %>%
+              weight = 1, popup = ~ name) %>%
   addPolylines(data = macleish_layers[["trails"]], 
                weight = 1, color = "brown",
-               popup = ~ trl_name) %>%
+               popup = ~ name) %>%
   addPolylines(data = macleish_layers[["streams"]], 
-               weight = 2)
+               weight = 2) %>%
+  addMarkers(data = subset(macleish_layers[["landmarks"]], grepl("Met", Label)), 
+             popup = ~Label)
 ```

### 2016-04-26 R/data.R

@@ -10,27 +10,44 @@
 #' The \code{WhatelyMet} station is located at (42.448470, -72.680553) and
 #' the \code{OrchardMet} station is at (42.449653, -72.680315).
 #' 
-#' Solar radiation is measured in two different ways: see \code{SlrW_Avg}
-#' or the \code{PAR} variables for Photosynthetic Active Radiation.
+#' \code{WhatelyMet} is located at the end of Poplar Hill Road in Whately, 
+#' Massachusetts, USA. The meteorological instruments of \code{WhatelyMet} (except the 
+#' rain gauge) are mounted at the top of a tower 25.3 m tall, well above the 
+#' surrounding forest canopy. The tower is located on a local ridge at an 
+#' elevation 250.75m above sea level.
+#' 
+#' \code{OrchardMet} is located about 250 m north of the first tower in an open 
+#' field next to an apple orchard. Full canopy trees (~20 m tall) are within 
+#' 30 m of this station. This station has a standard instrument configuration 
+#' with temperature, relative humidity, solar radiation, and barometric 
+#' pressure measured between 1.5 and 2.0 m above the ground. Wind speed and 
+#' direction are measured on a 10 m tall tower and precipitation is measured 
+#' on the ground. Ground temperature is measured at 15 and 30 cm below the 
+#' ground surface 2 m south of the tower. The tower is located 258.1 m above 
+#' sea level. Data collection at OrchardMet began on June 27th, 2014. 
+#' 
+#' The variables shown above are weather data collected at \code{WhatelyMet} and 
+#' \code{OrchardMet} during 2015. Solar radiation is measured in two different ways: 
+#' see \code{SlrW_Avg}or the \code{PAR} variables for Photosynthetic Active Radiation.
 #' 
 #' @docType data
-#' @format A data frame with 52,566 rows and 9 variables.
+#' @format For both, a data frame (\code{\link[dplyr]{tbl_df}}) with roughly 52,560 rows and 8 or 9 variables.
 #' 
-#' The following variables are values that are found in both Whately and Orchard data tables.
+#' The following variables are values that are found in either the \code{whately_2015}
+#' or \code{orchard_2015} data tables.
 #' 
 #' All variables are averaged over the 10 minute inverval unless otherwise noted.
 #' \describe{
-#'   \item{when}{timestamp for each measurment set.}
[…]

### 2016-04-26 R/etl_extract.R

@@ -71,7 +71,7 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Press_mb_Avg = ~as.numeric(Press_mb_Avg)) %>%
     mutate_(SlrW_Avg = ~as.numeric(SlrW_Avg)) %>%
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
-    distinct()
+    unique()
   write.csv(out, file = paste0(attr(obj, "load_dir"), "/whately.csv"), row.names = FALSE)
   # Orchard
   lcl <- paste0(attr(obj, "raw_dir"), "/OrchardMet_Met_10min.dat")
@@ -89,7 +89,7 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(PAR_Den_Avg = ~as.numeric(PAR_Den_Avg)) %>%
     mutate_(PAR_Tot_Avg = ~as.numeric(PAR_Tot_Avg)) %>%
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
-    distinct()
+    unique()
   write.csv(out, file = paste0(attr(obj, "load_dir"), "/orchard.csv"), row.names = FALSE)
   invisible(obj)
 }

### 2016-05-07 README.Rmd
added picture and updated README

@@
 The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
-Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.
 More information can be found at (http://www.smith.edu/ceeds/macleish.php)
 
-This R package allows you to download and process weather data (as a time series) using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station.
+![MacLeish Field Station](inst/extdata/macleish_600px.jpg)
+
+This R package allows you to download and process weather data using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station.
 It also contains shapefiles for contextualizing spatial information.

### 2016-05-07 R/data.R
Re-organized vignette and fixed NAMESPACE

@@ -30,6 +30,9 @@
 #' \code{OrchardMet} during 2015. Solar radiation is measured in two different ways: 
 #' see \code{SlrW_Avg}or the \code{PAR} variables for Photosynthetic Active Radiation.
 #' 
+#' Note that a loose wire resulted in erroneous temperature reading at OrchardMet
+#' in late November, 2015. 
+#' 
 #' @docType data
 #' @format For both, a data frame (\code{\link[dplyr]{tbl_df}}) with roughly 52,560 rows and 8 or 9 variables.
 #' 
@@ -53,6 +56,15 @@
 "whately_2015"
 
 #' @rdname whately_2015
+#' @examples 
+#' 
+#' # loose wire anomalies
+#' if (require(ggplot2)) {
+#'  orchard_2015 %>%
+#'  filter(month(when) == 11) %>%
+#'    ggplot(aes(x = when, y = Temp_C_Avg)) +
+#'    geom_line() + geom_smooth()
+#' }
 "orchard_2015"
 
 #' MacLeish spatial data

### 2016-05-07 R/etl_extract.R

@@ -3,6 +3,7 @@
 #' @description Retrieve data from the Macleish Field Station weather monitors
 #' @inheritParams etl::etl_extract
 #' @import etl
+#' @importFrom utils download.file
 #' @export
 #' @examples 
 #' 
@@ -45,13 +46,14 @@ etl_extract.etl_macleish <- function(obj, ...) {
   files <- c("WhatelyMet_Met_10min.dat", "OrchardMet_Met_10min.dat")
   src <- paste0(url, files)
   lcl <- paste0(attr(obj, "raw_dir"), "/", files)
-  mapply(download.file, src, lcl)
+  mapply(utils::download.file, src, lcl)
   invisible(obj)
 }
 
 #' @rdname etl_extract.etl_macleish
 #' @import dplyr
 #' @importFrom lubridate ymd_hms
+#' @importFrom utils head read.csv write.csv
 #' @export
 
 

### 2016-05-07 R/data.R
fixed example

@@ -59,7 +59,7 @@
 #' @examples 
 #' 
 #' # loose wire anomalies
-#' if (require(ggplot2)) {
+#' if (require(ggplot2) & require(lubridate)) {
 #'  orchard_2015 %>%
 #'  filter(month(when) == 11) %>%
 #'    ggplot(aes(x = when, y = Temp_C_Avg)) +

### 2016-05-07 README.Rmd
changed temperature; #15

@@
   group_by(the_year) %>%
-  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
+  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
 orchard <- macleish %>%
@@
   group_by(the_year) %>%
-  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
+  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
 ```
@@
   group_by(the_date) %>%
-  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
+  summarize(N = n(), avgTemp = mean(temperature)) %>%
   collect()

### 2016-05-07 R/data.R

@@ -42,7 +42,7 @@
 #' All variables are averaged over the 10 minute inverval unless otherwise noted.
 #' \describe{
 #'   \item{when}{Timestamp for each measurment set.}
-#'   \item{Temp_C_Avg}{average temperature, in Celsius}
+#'   \item{temperature}{average temperature, in Celsius}
 #'   \item{WSpd_mps}{Wind speed, in meters per second}
 #'   \item{Wdir_deg}{Wind direction, in degrees}
 #'   \item{RH_per_Avg}{How much water there is in the air, in millimeters}
@@ -62,7 +62,7 @@
 #' if (require(ggplot2) & require(lubridate)) {
 #'  orchard_2015 %>%
 #'  filter(month(when) == 11) %>%
-#'    ggplot(aes(x = when, y = Temp_C_Avg)) +
+#'    ggplot(aes(x = when, y = temperature)) +
 #'    geom_line() + geom_smooth()
 #' }
 "orchard_2015"

### 2016-05-07 R/etl_extract.R

@@ -21,9 +21,9 @@
 #'   tbl("orchard") 
 #'   
 #' whately %>%
-#'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
+#'   summarize(N = n(), avg_temp = mean(temperature))
 #' orchard %>%
-#'   summarize(N = n(), avg_temp = mean(Temp_C_Avg))
+#'   summarize(N = n(), avg_temp = mean(temperature))
 #'   
 #' # check data types
 #' whately %>%
@@ -67,6 +67,7 @@ etl_transform.etl_macleish <- function(obj, ...) {
     rename_(when = ~TIMESTAMP) %>%
     mutate_(when = ~ymd_hms(when)) %>%
     mutate_(Temp_C_Avg = ~as.numeric(Temp_C_Avg)) %>%
+    rename_(temperature = ~Temp_C_Avg) %>%
     mutate_(WSpd_mps = ~as.numeric(WSpd_mps)) %>%
     mutate_(Wdir_deg = ~as.numeric(Wdir_deg)) %>%
     mutate_(RH_per_Avg = ~as.numeric(RH_per_Avg)) %>%
@@ -84,6 +85,7 @@ etl_transform.etl_macleish <- function(obj, ...) {
     rename_(when = ~TIMESTAMP) %>%
     mutate_(when = ~ymd_hms(when)) %>%
     mutate_(Temp_C_Avg = ~as.numeric(Temp_C_Avg)) %>%
+    rename_(temperature = ~Temp_C_Avg) %>%
     mutate_(WSpd_mps = ~as.numeric(WSpd_mps)) %>%
     mutate_(Wdir_deg = ~as.numeric(Wdir_deg)) %>%
     mutate_(RH_per_Avg = ~as.numeric(RH_per_Avg)) %>%

### 2016-05-09 R/data.R
fixed example

@@ -58,12 +58,14 @@
 #' @rdname whately_2015
 #' @examples 
 #' 
-#' # loose wire anomalies
-#' if (require(ggplot2) & require(lubridate)) {
+#' \dontrun{
+#' #' # loose wire anomalies
+#' if (require(dplyr) & require(ggplot2) & require(lubridate)) {
 #'  orchard_2015 %>%
 #'  filter(month(when) == 11) %>%
 #'    ggplot(aes(x = when, y = temperature)) +
 #'    geom_line() + geom_smooth()
+#' }
 #' }
 "orchard_2015"
 

### 2016-05-10 R/data.R
close #15

@@ -43,14 +43,14 @@
 #' \describe{
 #'   \item{when}{Timestamp for each measurment set.}
 #'   \item{temperature}{average temperature, in Celsius}
-#'   \item{WSpd_mps}{Wind speed, in meters per second}
-#'   \item{Wdir_deg}{Wind direction, in degrees}
-#'   \item{RH_per_Avg}{How much water there is in the air, in millimeters}
-#'   \item{Press_mb_Avg}{Atmospheric pressure, in millibars}
-#'   \item{Rain_mm_Tot}{Total rainfall, in millimeters}
-#'   \item{SlrW_Avg}{Amount of radiation coming from the sun, in Watts/meters^2. Solar measurement for Whatley}
-#'   \item{PAR_Den_Avg}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average density of Watts/meters^2. One of two solar measurements for Orchard}
-#'   \item{PAR_Tot_Avg}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average total over measurement period of Watts/meters^2. One of two solar measurements for Orchard}
+#'   \item{wind_speed}{Wind speed, in meters per second}
+#'   \item{wind_dir}{Wind direction, in degrees}
+#'   \item{rel_humidity}{How much water there is in the air, in millimeters}
+#'   \item{pressure}{Atmospheric pressure, in millibars}
+#'   \item{rainfall}{Total rainfall, in millimeters}
+#'   \item{solar_radiation}{Amount of radiation coming from the sun, in Watts/meters^2. Solar measurement for Whatley}
+#'   \item{par_density}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average density of Watts/meters^2. One of two solar measurements for Orchard}
+#'   \item{par_total}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average total over measurement period of Watts/meters^2. One of two solar measurements for Orchard}
 #' }
 #' @source These data are recorded at \url{http://www.smith.edu/ceeds/macleish_monitoring.php} 
 "whately_2015"

### 2016-05-10 R/etl_extract.R

@@ -69,11 +69,17 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Temp_C_Avg = ~as.numeric(Temp_C_Avg)) %>%
     rename_(temperature = ~Temp_C_Avg) %>%
     mutate_(WSpd_mps = ~as.numeric(WSpd_mps)) %>%
+    rename_(wind_speed = ~WSpd_mps) %>%
     mutate_(Wdir_deg = ~as.numeric(Wdir_deg)) %>%
+    rename_(wind_dir = ~Wdir_deg) %>%
     mutate_(RH_per_Avg = ~as.numeric(RH_per_Avg)) %>%
+    rename_(rel_humidity = ~RH_per_Avg) %>%
     mutate_(Press_mb_Avg = ~as.numeric(Press_mb_Avg)) %>%
+    rename_(pressure = ~Press_mb_Avg) %>%
     mutate_(SlrW_Avg = ~as.numeric(SlrW_Avg)) %>%
+    rename_(solar_radiation = ~SlrW_Avg) %>%
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
+    rename_(rainfall = ~Rain_mm_Tot) %>%
     unique()
   write.csv(out, file = paste0(attr(obj, "load_dir"), "/whately.csv"), row.names = FALSE)
   # Orchard
@@ -87,12 +93,19 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Temp_C_Avg = ~as.numeric(Temp_C_Avg)) %>%
     rename_(temperature = ~Temp_C_Avg) %>%
     mutate_(WSpd_mps = ~as.numeric(WSpd_mps)) %>%
+    rename_(wind_speed = ~WSpd_mps) %>%
     mutate_(Wdir_deg = ~as.numeric(Wdir_deg)) %>%
+    rename_(wind_dir = ~Wdir_deg) %>%
     mutate_(RH_per_Avg = ~as.numeric(RH_per_Avg)) %>%
+    rename_(rel_humidity = ~RH_per_Avg) %>%
     mutate_(Press_mb_Avg = ~as.numeric(Press_mb_Avg)) %>%
+    rename_(pressure = ~Press_mb_Avg) %>%
     mutate_(PAR_Den_Avg = ~as.numeric(PAR_Den_Avg)) %>%
[…]

### 2016-05-10 data-raw/weather.R

@@ -1,6 +1,6 @@
 # Creates 2015 data for Whately and Orchard
 
-macleish <- etl("macleish") %>%
+macleish <- etl("macleish", dir = "~/Desktop/macleish/") %>%
   etl_extract() %>%
   etl_transform() %>%
   etl_load()

### 2016-05-10 README.Rmd
faster loading readr and dbWriteTable directly from file

--- 2016-05-07 README.Rmd
@@
 whately %>%
-  mutate(the_year = strftime('%Y', when, 'unixepoch')) %>%
+  mutate(the_year = strftime('%Y', when)) %>%
   group_by(the_year) %>%
-  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
+  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
 orchard <- macleish %>%
@@
 orchard %>%
-  mutate(the_year = strftime('%Y', when, 'unixepoch')) %>%
+  mutate(the_year = strftime('%Y', when)) %>%
   group_by(the_year) %>%
-  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
+  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
 ```
@@
 daily <- whately %>%
-  mutate(the_date = date(when, 'unixepoch')) %>%
+  mutate(the_date = date(when)) %>%
   group_by(the_date) %>%
-  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
+  summarize(N = n(), avgTemp = mean(temperature)) %>%
   collect()

### 2016-05-10 R/etl_extract.R

@@ -53,14 +53,15 @@ etl_extract.etl_macleish <- function(obj, ...) {
 #' @rdname etl_extract.etl_macleish
 #' @import dplyr
 #' @importFrom lubridate ymd_hms
-#' @importFrom utils head read.csv write.csv
+#' @importFrom readr read_csv write_csv
+#' @importFrom utils head
 #' @export
 
 
 etl_transform.etl_macleish <- function(obj, ...) {
   # Whately
   lcl <- paste0(attr(obj, "raw_dir"), "/WhatelyMet_Met_10min.dat")
-  x <- read.csv(lcl, skip = 1, stringsAsFactors = FALSE)
+  x <- readr::read_csv(lcl, skip = 1)
   metadata <- head(x, 2)
   out <- x[-(1:2), -2]
   out <- out %>%
@@ -81,10 +82,10 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
     rename_(rainfall = ~Rain_mm_Tot) %>%
     unique()
-  write.csv(out, file = paste0(attr(obj, "load_dir"), "/whately.csv"), row.names = FALSE)
+  readr::write_csv(out, path = paste0(attr(obj, "load_dir"), "/whately.csv"))
   # Orchard
   lcl <- paste0(attr(obj, "raw_dir"), "/OrchardMet_Met_10min.dat")
-  x <- read.csv(lcl, skip = 1, stringsAsFactors = FALSE)
+  x <- readr::read_csv(lcl, skip = 1)
   metadata <- head(x, 2)
   out <- x[-(1:2), -2]
   out <- out %>%
@@ -107,7 +108,7 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
     rename_(rainfall = ~Rain_mm_Tot) %>%
     unique()
-  write.csv(out, file = paste0(attr(obj, "load_dir"), "/orchard.csv"), row.names = FALSE)
+  readr::write_csv(out, path = paste0(attr(obj, "load_dir"), "/orchard.csv"))
   invisible(obj)
 }
 
@@ -118,21 +119,17 @@ etl_transform.etl_macleish <- function(obj, ...) {
 
 etl_load.etl_macleish <- function(obj, ...) {
   # Whately
[…]

### 2016-05-10 data-raw/weather.R

@@ -8,18 +8,18 @@ macleish <- etl("macleish", dir = "~/Desktop/macleish/") %>%
 # Do the date computations in SQLite to save memory
 whately_2015 <- macleish %>%
   tbl("whately") %>%
-  mutate(the_datetime = datetime(when, 'unixepoch')) %>%
-  mutate(the_year = as.numeric(strftime('%Y', when, 'unixepoch'))) %>%
+  mutate(the_datetime = datetime(when)) %>%
+  mutate(the_year = as.numeric(strftime('%Y', when))) %>%
   filter(the_year == 2015) %>%
   collect() %>%
-  mutate(when = as.POSIXct(the_datetime)) %>%
+  mutate(when = lubridate::ymd_hms(the_datetime)) %>%
   select(-the_datetime, -the_year)
 
 # collect first and do the date computations in R
 orchard_2015 <- macleish %>%
   tbl("orchard") %>%
   collect() %>%
-  mutate(when = as.POSIXct(when, origin = "1970-01-01")) %>%
+  mutate(when = lubridate::ymd_hms(when)) %>%
   filter(lubridate::year(when) == 2015)
 
 save(whately_2015, file = "data/whately_2015.rda", compress = "xz")

### 2016-05-11 R/data.R
added broken timestamp correction; #8

@@ -41,7 +41,7 @@
 #' 
 #' All variables are averaged over the 10 minute inverval unless otherwise noted.
 #' \describe{
-#'   \item{when}{Timestamp for each measurment set.}
+#'   \item{when}{Timestamp for each measurment set in Eastern Standard Time.}
 #'   \item{temperature}{average temperature, in Celsius}
 #'   \item{wind_speed}{Wind speed, in meters per second}
 #'   \item{wind_dir}{Wind direction, in degrees}

### 2016-05-11 R/etl_extract.R

@@ -82,6 +82,8 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
     rename_(rainfall = ~Rain_mm_Tot) %>%
     unique()
+  out <- out %>%
+    mutate_(when = ~ifelse(when < '2012-12-20 05:20:00', when - lubridate::dhours(5), when))
   readr::write_csv(out, path = paste0(attr(obj, "load_dir"), "/whately.csv"))
   # Orchard
   lcl <- paste0(attr(obj, "raw_dir"), "/OrchardMet_Met_10min.dat")

### 2016-05-12 R/etl_extract.R
corrected time stamps for the first 50682 rows #8

@@ -83,8 +83,11 @@ etl_transform.etl_macleish <- function(obj, ...) {
     rename_(rainfall = ~Rain_mm_Tot) %>%
     unique()
   out <- out %>%
-    mutate_(when = ~ifelse(when < '2012-12-20 05:20:00', when - lubridate::dhours(5), when))
+    mutate(num = seq(1, length.out=nrow(out), by=1)) %>%
+    mutate(when = ifelse(num <= 50682, when - dhours(5), when)) %>%
+    mutate(when = as.POSIXct(when, origin = "1970-01-01 00:00:00")) 
   readr::write_csv(out, path = paste0(attr(obj, "load_dir"), "/whately.csv"))
+  
   # Orchard
   lcl <- paste0(attr(obj, "raw_dir"), "/OrchardMet_Met_10min.dat")
   x <- readr::read_csv(lcl, skip = 1)

### 2016-05-12 R/etl_extract.R
corrected time stamps for orchard

@@ -95,7 +95,7 @@ etl_transform.etl_macleish <- function(obj, ...) {
   out <- x[-(1:2), -2]
   out <- out %>%
     rename_(when = ~TIMESTAMP) %>%
-    mutate_(when = ~ymd_hms(when)) %>%
+    mutate_(when = ~as.integer(ymd_hms(when))) %>%
     mutate_(Temp_C_Avg = ~as.numeric(Temp_C_Avg)) %>%
     rename_(temperature = ~Temp_C_Avg) %>%
     mutate_(WSpd_mps = ~as.numeric(WSpd_mps)) %>%
@@ -113,6 +113,12 @@ etl_transform.etl_macleish <- function(obj, ...) {
     mutate_(Rain_mm_Tot = ~as.numeric(Rain_mm_Tot)) %>%
     rename_(rainfall = ~Rain_mm_Tot) %>%
     unique()
+  out<- out %>%
+    mutate(num = seq(1, length.out=nrow(orcharddata), by=1)) %>%
+    mutate(when = ifelse( num >= 18482, when + dhours(1), when)) %>%
+    mutate(when = ifelse( num >= 70892, when + dminutes(50), when)) %>%
+    mutate(when = as.POSIXct(when, origin = "1970-01-01 00:00:00"))
+  
   readr::write_csv(out, path = paste0(attr(obj, "load_dir"), "/orchard.csv"))
   invisible(obj)
 }

### 2016-06-07 R/data.R
removed steep slopes in preparation for CRAN submission

@@ -93,7 +93,6 @@
 #'  \item{buildings}{Buildings at MacLeish}
 #'  \item{wetlands}{Wetland areas}
 #'  \item{trails}{Hiking trails}
-#'  \item{slopes}{steep slopes}
 #'  \item{schools}{Schools in Massachusetts}
 #'  \item{boundary}{the property boundary}
 #'  \item{research}{research plots}

### 2016-06-07 data-raw/spatial.R

@@ -15,7 +15,8 @@ ogrInfo(dsn, layer = "trails")
 layers <- c("landmarks", "forests", "streams",
   "challenge_courses", 
   "buildings", "wetlands",
-  "slopes", "boundary", 
+#  "slopes", 
+  "boundary", 
   "research", "soil", "trails")
 
 macleish_layers <- lapply(layers, readOGR, dsn = dsn)

### 2016-06-08 tests/testthat.R
updated Travis, added tests

@@ -1,0 +1,4 @@
+library(testthat)
+library(macleish)
+
+test_check("macleish")

### 2016-06-08 tests/testthat/test-macleish.R

@@ -1,0 +1,12 @@
+context("macleish")
+
+## TODO: Rename context
+## TODO: Add more tests
+
+test_that("data integrity", {
+  expect_is(whately_2015, "tbl_df")
+  expect_is(orchard_2015, "tbl_df")
+  expect_equal(nrow(whately_2015), 6*24*365)
+  expect_length(macleish_layers, 10)
+  expect_equal(unique(sapply(macleish_layers, sp::proj4string)), "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")
+})

### 2016-06-09 README.Rmd
updated DESCRIPTION and README
version bump and updated README with CRAN badge

@@
 [![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)
 
@@
 ```{r, eval=FALSE}
-# install.packages("devtools")
-devtools::install_github("beanumber/etl")
-devtools::install_github("beanumber/macleish")
+install.packages("macleish")
 ```

### 2017-09-28 R/data.R
corrected spelling

@@ -39,7 +39,7 @@
 #' The following variables are values that are found in either the \code{whately_2015}
 #' or \code{orchard_2015} data tables.
 #' 
-#' All variables are averaged over the 10 minute inverval unless otherwise noted.
+#' All variables are averaged over the 10 minute interval unless otherwise noted.
 #' \describe{
 #'   \item{when}{Timestamp for each measurment set in Eastern Standard Time.}
 #'   \item{temperature}{average temperature, in Celsius}
@@ -48,7 +48,7 @@
 #'   \item{rel_humidity}{How much water there is in the air, in millimeters}
 #'   \item{pressure}{Atmospheric pressure, in millibars}
 #'   \item{rainfall}{Total rainfall, in millimeters}
-#'   \item{solar_radiation}{Amount of radiation coming from the sun, in Watts/meters^2. Solar measurement for Whatley}
+#'   \item{solar_radiation}{Amount of radiation coming from the sun, in Watts/meters^2. Solar measurement for Whately}
 #'   \item{par_density}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average density of Watts/meters^2. One of two solar measurements for Orchard}
 #'   \item{par_total}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average total over measurement period of Watts/meters^2. One of two solar measurements for Orchard}
 #' }

### 2018-03-27 R/data.R
updated package to sf

@@ -73,15 +73,15 @@
 #' 
 #' @description Shapefiles from the MacLeish Field Station. The field station
 #' itself is located at \code{lat = 42.449167}, \code{lon = -72.679389}. These
-#' data contains information about various man-made and natural structures
+#' data contain information about various man-made and natural structures
 #' surrounding the field station. 
 #' 
-#' @details Each of the \code{\link[sp]{Spatial}} objects are projected in 
+#' @details Each of the \code{\link[sf]{sf}} objects are projected in 
 #' \code{epsg:4326} for easy integration with \code{\link[ggmap]{ggmap}} or
 #' \code{\link[leaflet]{leaflet}} objects. 
 #' 
 #' @docType data
-#' @format A \code{list} of \code{\link[sp]{Spatial}} objects, each providing a different layer.
+#' @format A \code{list} of \code{\link[sf]{sf}} objects, each providing a different layer.
 #' 
 #' \describe{
 #'  \item{landmarks}{Landmarks}
@@ -101,9 +101,9 @@
 #' 
 #' @examples 
 #' names(macleish_layers)
-#' summary(macleish_layers[["buildings"]])
+#' macleish_layers[["buildings"]]
 #' 
-#' if (require(sp)) {
+#' if (require(sf)) {
 #'  plot(macleish_layers[["buildings"]])
 #' }
 #' 

### 2018-03-27 data-raw/spatial.R

@@ -19,7 +19,9 @@ layers <- c("landmarks", "forests", "streams",
   "boundary", 
   "research", "soil", "trails")
 
-macleish_layers <- lapply(layers, readOGR, dsn = dsn)
+
+library(sf)
+macleish_layers <- lapply(layers, st_read, dsn = dsn)
 names(macleish_layers) <- layers
 
 # names(macleish_layers) <- c("landmarks", "forests", "streams",
@@ -29,7 +31,7 @@ names(macleish_layers) <- layers
 #                             "research", "soil", "trails")
 
 # check to make sure they are all projected the same
-lapply(macleish_layers, proj4string)
+sapply(macleish_layers, st_crs)
 
 # fix the projection string
 # proj4string(macleish_layers[[10]]) <- proj4string(macleish_layers[[1]])

### 2018-03-27 tests/testthat/test-macleish.R

@@ -8,5 +8,13 @@ test_that("data integrity", {
   expect_is(orchard_2015, "tbl_df")
   expect_equal(nrow(whately_2015), 6*24*365)
   expect_length(macleish_layers, 10)
-  expect_equal(unique(sapply(macleish_layers, sp::proj4string)), "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")
+  macleish_layers %>%
+    sapply(FUN = sf::st_crs) %>%
+    t() %>%
+    as_data_frame() %>%
+    bind_rows() %>%
+    pull("proj4string") %>%
+    unlist() %>%
+    unique() %>%
+    expect_equal("+proj=longlat +datum=WGS84 +no_defs")
 })

### 2018-03-27 README.Rmd
updated NEWS and README

@@
                weight = 2) %>%
-  addMarkers(data = subset(macleish_layers[["landmarks"]], grepl("Met", Label)), 
+  addMarkers(data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
              popup = ~Label)

### 2019-05-20 R/data.R
fixed typos and broken link

@@ -41,7 +41,7 @@
 #' 
 #' All variables are averaged over the 10 minute interval unless otherwise noted.
 #' \describe{
-#'   \item{when}{Timestamp for each measurment set in Eastern Standard Time.}
+#'   \item{when}{Timestamp for each measurement set in Eastern Standard Time.}
 #'   \item{temperature}{average temperature, in Celsius}
 #'   \item{wind_speed}{Wind speed, in meters per second}
 #'   \item{wind_dir}{Wind direction, in degrees}

### 2020-08-28 data-raw/sticker.R
drafted hex sticker

@@ -1,0 +1,20 @@
+library(hexSticker)
+library(magick)
+
+library(macleish)
+library(ggplot2)
+library(sf)
+
+p <- ggplot(macleish_layers[["boundary"]]) +
+  geom_sf(fill = "#94946C") +
+  theme_void()
+
+p %>%
+  sticker(
+    package = "macleish", p_color = "#5F6B65", h_color = "#5F6B65", h_fill = "#FFFFFF",
+    p_y = 1.6,
+    filename = here::here("data-raw", "hex_macleish.png"),
+    p_size = 16, s_x = 1, s_y = .75, s_width = 1.3, s_height = 1.3
+  )
+
+

### 2020-08-28 README.Rmd
drafted hex sticker
updated README

@@
 ---
-title: "MacLeish"
 output:
@@
 
+# macleish <img src='man/figures/logo.png' align="right" height="139" />
+
 [![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)
@@
 
-The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
-More information can be found at (http://www.smith.edu/ceeds/macleish.php)
+The [Ada and Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
 
@@
   summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
+
 orchard <- macleish %>%
@@
   collect()
+
 library(ggplot2)
@@
   addTiles() %>%
-  addPolygons(data = macleish_layers[["boundary"]], 
-              weight = 1, fillOpacity = 0.1) %>%
-  addPolygons(data = macleish_layers[["buildings"]], 
-              weight = 1, popup = ~ name) %>%
-  addPolylines(data = macleish_layers[["trails"]], 
+  addPolygons(
+    data = macleish_layers[["boundary"]], 
+    weight = 1, fillOpacity = 0.1
+  ) %>%
+  addPolygons(
+    data = macleish_layers[["buildings"]], 
+    weight = 1, popup = ~ name
+  ) %>%
+  addPolylines(
+    data = macleish_layers[["trails"]], 
     weight = 1, color = "brown",
-               popup = ~ name) %>%
-  addPolylines(data = macleish_layers[["streams"]], 
-               weight = 2) %>%
-  addMarkers(data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
-             popup = ~Label)
+    popup = ~ name
+  ) %>%
+  addPolylines(
+    data = macleish_layers[["streams"]], 
+    weight = 2
+  ) %>%
+  addMarkers(
+    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
+    popup = ~Label
+  )
 ```
+
+## See also
+
+- [Ada and Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php)
+- **[etl](https://www.github.com/beanumber/etl)**

### 2020-08-28 data-raw/sticker.R
made package name bigger

@@ -12,9 +12,9 @@ p <- ggplot(macleish_layers[["boundary"]]) +
 p %>%
   sticker(
     package = "macleish", p_color = "#5F6B65", h_color = "#5F6B65", h_fill = "#FFFFFF",
-    p_y = 1.6,
+    p_y = 1.53,
     filename = here::here("data-raw", "hex_macleish.png"),
-    p_size = 16, s_x = 1, s_y = .75, s_width = 1.3, s_height = 1.3
+    p_size = 24, s_x = 1, s_y = .75, s_width = 1.3, s_height = 1.3
   )
 
 

### 2020-08-28 data-raw/sticker.R
bert's ideas about sticker

@@ -7,14 +7,23 @@ library(sf)
 
 p <- ggplot(macleish_layers[["boundary"]]) +
   geom_sf(fill = "#94946C") +
-  theme_void()
+  geom_sf(data = macleish_layers[["streams"]], color = "dodgerblue") + 
+  geom_sf(data = macleish_layers[["trails"]], color = "#5F6B65") + 
+  theme_void() + 
+  ylim(c(42.44, 42.46))
 
-p %>%
+macleish_sticker <- p %>%
   sticker(
     package = "macleish", p_color = "#5F6B65", h_color = "#5F6B65", h_fill = "#FFFFFF",
     p_y = 1.53,
     filename = here::here("data-raw", "hex_macleish.png"),
-    p_size = 24, s_x = 1, s_y = .75, s_width = 1.3, s_height = 1.3
-  )
+    p_size = 24, s_x = 1, s_y = .75, s_width = 1.3, s_height = 1.3,
+    white_around_sticker = TRUE,
+    url = "github.com/beanumber/macleish", u_size = 4
+  ) + 
+  geom_pkgname(package = "ma", color = "dodgerblue", y = 1.53, size = 24, x = 0.59)
+
+save_sticker(here::here("data-raw", "hex_macleish.png"), macleish_sticker)
+
 
 

### 2021-06-07 README.Rmd
trivial change
switch travis to github actions

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)
+[![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
 [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)

### 2021-06-11 R/MacLeish_Data_Plot_MC_01.R
Issues with documenting uploaded datasets

@@ -1,0 +1,21 @@
+
+
+\docType{data}
+\name{maple_sap}
+\alias{maple_sap}
+\title{Maple sap collection at MacLeish}
+\format{
+  \describe{
+    \item{when}{the date of collection}
+    \item{sap}{how much sap was collected, in gallons}
+    \item{Comments}{comments}
+    \item{People}{who was there?}
+  }
+}
+\usage{
+  maple_sap
+}
+\description{
+  Maple sap collection at MacLeish
+}
+\keyword{datasets} 

### 2021-06-11 R/data.R

@@ -121,3 +121,14 @@
 #'  \item{People}{who was there?}
 #' }
 "maple_sap"
+
+#' Plot data collection at MacLeish
+#' @docType data
+#' @format 
+#' \describe {
+#'  \item{when}{the date of collection}
+#'  \item{sap}{how much sap was collected, in gallons}
+#'  \item{Comments}{comments}
+#'  \item{People}{who was there?}
+#'  }
+"MacLeish_Data_Plot_MC_01"

### 2021-06-11 data-raw/Download.Rmd
Updated instructions

---
title: "Untitled"
author: "Dominique Kelly"
date: "6/3/2021"
output: html_document
---

```{r setup, include=FALSE}
#update.packages(ask = FALSE, checkBuilt = TRUE)
```

Check out this as an example: https://github.com/rudeboybert/fivethirtyeight/blob/master/data-raw/process_data_sets.R

Note:
* You'll be reading in an excel file, not a .csv
* Then make sure usethis::use_data() works
* Then do data cleaning

```{r}
usethis::use_data(MacLeish_Data_Plot_MC_01, overwrite = TRUE)
usethis::use_data(MacLeish_Data_Plot_MC_02, overwrite = TRUE)
```

```{r}
load_all()
```

```{r}
library(devtools)
library(tidyverse)
library(fs)
```

```{r}
plot_data <- as_tibble(MacLeish_Data_Plot_MC_01)
plot_data
```

### 2021-06-11 data-raw/Download.Rmd
updated instructions

@@
 
-Check out this as an example: https://github.com/rudeboybert/fivethirtyeight/blob/master/data-raw/process_data_sets.R
+Check out thes as an example:
+
+* https://github.com/rudeboybert/fivethirtyeight/blob/master/data-raw/process_data_sets.R to load data into package
+* https://github.com/rudeboybert/fivethirtyeight/blob/master/R/data.R#L22 to write help file using `roxygen2`
 

### 2021-06-12 R/data.R
Uploaded Jesse's data into R and tidy the data

@@ -122,13 +122,3 @@
 #' }
 "maple_sap"
 
-#' Plot data collection at MacLeish
-#' @docType data
-#' @format 
-#' \describe {
-#'  \item{when}{the date of collection}
-#'  \item{sap}{how much sap was collected, in gallons}
-#'  \item{Comments}{comments}
-#'  \item{People}{who was there?}
-#'  }
-"MacLeish_Data_Plot_MC_01"

### 2021-06-12 R/plot_data.R

@@ -1,0 +1,79 @@
+library(readxl)
+
+#Uploading data into R
+plot_data01 <- read_excel("data-raw/MacLeish Data_Plot MC-01.xlsx")
+plot_data02 <- read_excel("data-raw/MacLeish Data_Plot MC-02.xlsx")
+
+usethis::use_data(plot_data01, overwrite = TRUE)
+usethis::use_data(plot_data02, overwrite = TRUE)
+
+library(tidyverse)
+library(janitor)
+library(lubridate)
+library(stringr)
+library(usethis)
+library(devtools)
+library(dplyr)
+
+#Plot Data 1
+#Creating year and height column 
+newplot_data01 <- plot_data01 %>%
+  pivot_longer(c(`Fall'15`, `Fall'14`,`Fall'13`,`Fall'12`,`Fall'11`,`Fall'10`), names_to = "Year", values_to = "Height")
+
+#Separating fall and year into new columns 
+newplot_data01 <- newplot_data01 %>%
+  separate(Year, c("Semester", "Year"), sep = 4)
+
+#Changing abbreviated year into full year 
+newplot_data01$Year[newplot_data01$Year == "'15"] <- "2015"
+newplot_data01$Year[newplot_data01$Year == "'14"] <- "2014"
+newplot_data01$Year[newplot_data01$Year == "'13"] <- "2013"
+newplot_data01$Year[newplot_data01$Year == "'12"] <- "2012"
+newplot_data01$Year[newplot_data01$Year == "'11"] <- "2011"
+newplot_data01$Year[newplot_data01$Year == "'10"] <- "2010"
+
+#Changing value "DEAD" to "0" for height 
+newplot_data01$Height[newplot_data01$Height == "DEAD"] <- "0"
+
+#Shifting the "Notes:" column to the end of the dataset 
+newplot_data01 <- newplot_data01 %>%
+  relocate("Notes:", .after = "Height")
+
+View(newplot_data01)
+
+plot_data01 <- newplot_data01
+
+usethis::use_data(plot_data01, overwrite = TRUE)
+
+
+#Plot Data 2
+library(readxl)
+plot_data02 <- read_excel("data-raw/MacLeish Data_Plot MC-02.xlsx")
+
+#Creating year and height column 
+newplot_data02 <- plot_data02 %>%
+  pivot_longer(c(`FALL 2016`, `Fall'12`,`Fall'11`,`Fall'10`,`Fall'09`), names_to = "Year", values_to = "Height")
+
[…]

### 2021-06-13 R/MacLeish_Data_Plot_MC_01.R
Documentation for plot data 1 and plot data 2

@@ -1,21 +1,0 @@
-
-
-\docType{data}
-\name{maple_sap}
-\alias{maple_sap}
-\title{Maple sap collection at MacLeish}
-\format{
-  \describe{
-    \item{when}{the date of collection}
-    \item{sap}{how much sap was collected, in gallons}
-    \item{Comments}{comments}
-    \item{People}{who was there?}
-  }
-}
-\usage{
-  maple_sap
-}
-\description{
-  Maple sap collection at MacLeish
-}
-\keyword{datasets} 

### 2021-06-13 R/data.R

@@ -122,3 +122,24 @@
 #' }
 "maple_sap"
 
+#' Plot data collection at MacLeish
+#' @docType data
+#' @format 
+#' \describe{
+#'  \item{when}{the date of collection}
+#'  \item{sap}{how much sap was collected, in gallons}
+#'  \item{Comments}{comments}
+#'  \item{People}{who was there?}
+#' }
+"plot_data01"
+
+#' Plot data collection at MacLeish
+#' @docType data
+#' @format 
+#' \describe{
+#'  \item{when}{the date of collection}
+#'  \item{sap}{how much sap was collected, in gallons}
+#'  \item{Comments}{comments}
+#'  \item{People}{who was there?}
+#' }
+"plot_data02"

### 2021-06-13 R/plot_data.R

@@ -77,3 +77,7 @@ View(newplot_data02)
 plot_data02 <- newplot_data02
 
 usethis::use_data(plot_data02, overwrite = TRUE)
+
+#Documentation complete:
+#Use plot_data01 and ?plot_data01 to see plot data01 documentation
+#Use plot_data02 and ?plot_data02 to see plot data02 documentation

### 2021-06-13 R/data.R
Updated help document for plot data 1 and 2, updated paper outline with working title and author order

@@ -126,10 +126,10 @@
 #' @docType data
 #' @format 
 #' \describe{
-#'  \item{when}{the date of collection}
-#'  \item{sap}{how much sap was collected, in gallons}
+#'  \item{when}{Data collected from 2010-2015}
+#'  \item{size}{20 x 50 m and divided into 10 subplot modules of 110 m} 
 #'  \item{Comments}{comments}
-#'  \item{People}{who was there?}
+#'  \item{People}{Jesse Bellemare}
 #' }
 "plot_data01"
 
@@ -137,9 +137,9 @@
 #' @docType data
 #' @format 
 #' \describe{
-#'  \item{when}{the date of collection}
-#'  \item{sap}{how much sap was collected, in gallons}
+#'  \item{when}{Data collected from 2009-2012}
+#'  \item{size}{20 x 50 m and divided into 10 subplot modules of 110 m}
 #'  \item{Comments}{comments}
-#'  \item{People}{who was there?}
+#'  \item{People}{Jesse Bellemare}
 #' }
 "plot_data02"

### 2021-06-21 R/data.R
Trival changes to plot datasets and created rough draft for paper

@@ -123,7 +123,7 @@
 "maple_sap"
 
 #' MacLeish Data Plot 1
-#' @description Collected data on the trend of tree diameter in centimeters 
+#' @description Collected data on change in tree diameter (in centimeters)
 #' for Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
 #' Tree diameter was measured at 1.4 meters high above the ground.
 #' @docType data
@@ -132,12 +132,12 @@
 #'  \item{When}{Data collected from 2010-2015 in the fall semesters.}
 #'  \item{Size}{20 x 50 m and divided into 10 subplot modules of 110 m. Five 10 x 10 modules along central 50 m axis.} 
 #'  \item{Comments}{comments}
-#'  \item{People}{Data obtained from Jesse Bellemare and Smith College students from BIO364-365 course.}
+#'  \item{People}{Data obtained from Jesse Bellemare and Smith College students from BIO364-365 courses.}
 #' }
 "plot_data01"
 
 #' MacLeish Data Plot 2
-#' @description Collected data on the trend of tree diameter in centimeters 
+#' @description Collected data on change in tree diameter (in centimeters) 
 #' for Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
 #' Tree diameter was measured at 1.4 meters high above the ground.
 #' @docType data
@@ -146,6 +146,6 @@
 #'  \item{When}{Data collected from 2009-2012 in the fall semesters.}
 #'  \item{Size}{20 x 50 m and divided into 10 subplot modules of 110 m. Five 10 x 10 modules along central 50 m axis.}
 #'  \item{Comments}{comments}
-#'  \item{People}{Data obtained from Jesse Bellemare and Smith College students from BIO364-365 course.}
+#'  \item{People}{Data obtained from Jesse Bellemare and Smith College students from BIO364-365 courses.}
 #' }
 "plot_data02"

### 2021-06-22 R/data.R
Renamed data, removed superfluous code, move all R package loading to top of file, documented other variables

@@ -123,29 +123,38 @@
 "maple_sap"
 
 #' MacLeish Data Plot 1
-#' @description Collected data on change in tree diameter (in centimeters)
-#' for Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
+#' @description Data on change in tree diameter (in centimeters)
+#' for parasitic Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
 #' Tree diameter was measured at 1.4 meters high above the ground.
 #' @docType data
 #' @format 
 #' \describe{
-#'  \item{When}{Data collected from 2010-2015 in the fall semesters.}
-#'  \item{Size}{20 x 50 m and divided into 10 subplot modules of 110 m. Five 10 x 10 modules along central 50 m axis.} 
-#'  \item{Comments}{comments}
+#'  \item{Module}{20 x 50 m and divided into 10 subplot modules of 110 m. There are five 10 x 10 modules along central 50 m axis.}
+#'  \item{Tag}{Tag numbers used to identify each tree.} 
+#'  \item{Species}{Tree species include Acer rubrum, Betula lenta, Betula papyrifera, Fagus grandifolia, Hamamelis virginiana, 
+#'  Pinus strobus, Quercus rubra, and Tsuga canadensis.}
+#'  \item{Position}{Stage of growth for each individual tree.}
+#'  \item{Year}{Data collected from 2010-2015 in the fall semesters.}
+#'  \item{Notes}{Notes collected on the wellbeing of tree species, including notes on death or poor health.}
+#'  \item{Diameter(cm)}{Tree diameter measured in centimeters and at 1.4 meters high above the ground.}
 #'  \item{People}{Data obtained from Jesse Bellemare and Smith College students from BIO364-365 courses.}
 #' }
-"plot_data01"
+"tree_diameter1"
 
 #' MacLeish Data Plot 2
-#' @description Collected data on change in tree diameter (in centimeters) 
-#' for Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
+#' @description Data on change in tree diameter (in centimeters) 
+#' for parasitic Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
 #' Tree diameter was measured at 1.4 meters high above the ground.
 #' @docType data
 #' @format 
 #' \describe{
-#'  \item{When}{Data collected from 2009-2012 in the fall semesters.}
[…]

### 2021-06-22 data-raw/plot_data.R

@@ -1,12 +1,4 @@
 library(readxl)
-
-#Uploading data into R
-plot_data01 <- read_excel("data-raw/MacLeish Data_Plot MC-01.xlsx")
-plot_data02 <- read_excel("data-raw/MacLeish Data_Plot MC-02.xlsx")
-
-usethis::use_data(plot_data01, overwrite = TRUE)
-usethis::use_data(plot_data02, overwrite = TRUE)
-
 library(tidyverse)
 library(janitor)
 library(lubridate)
@@ -15,69 +7,62 @@ library(usethis)
 library(devtools)
 library(dplyr)
 
+#Uploading data into R
+tree_diameter1 <- read_excel("data-raw/MacLeish Data_Plot MC-01.xlsx")
+tree_diameter2 <- read_excel("data-raw/MacLeish Data_Plot MC-02.xlsx")
+
 #Plot Data 1
 #Creating year and height column 
-newplot_data01 <- plot_data01 %>%
+tree_diameter1 <- tree_diameter1 %>%
   pivot_longer(c(`Fall'15`, `Fall'14`,`Fall'13`,`Fall'12`,`Fall'11`,`Fall'10`), names_to = "Year", values_to = "Diameter(cm)")
 
 #Separating fall and year into new columns 
-newplot_data01 <- newplot_data01 %>%
+tree_diameter1 <- tree_diameter1 %>%
   separate(Year, c("Semester", "Year"), sep = 4)
 
 #Changing abbreviated year into full year 
-newplot_data01$Year[newplot_data01$Year == "'15"] <- "2015"
-newplot_data01$Year[newplot_data01$Year == "'14"] <- "2014"
-newplot_data01$Year[newplot_data01$Year == "'13"] <- "2013"
-newplot_data01$Year[newplot_data01$Year == "'12"] <- "2012"
-newplot_data01$Year[newplot_data01$Year == "'11"] <- "2011"
-newplot_data01$Year[newplot_data01$Year == "'10"] <- "2010"
+tree_diameter1$Year[tree_diameter1$Year == "'15"] <- "2015"
+tree_diameter1$Year[tree_diameter1$Year == "'14"] <- "2014"
+tree_diameter1$Year[tree_diameter1$Year == "'13"] <- "2013"
+tree_diameter1$Year[tree_diameter1$Year == "'12"] <- "2012"
+tree_diameter1$Year[tree_diameter1$Year == "'11"] <- "2011"
[…]

### 2021-06-27 data-raw/plot_data.R
Added abstract in description

@@ -34,9 +34,6 @@ tree_diameter1$`Diameter(cm)`[tree_diameter1$`Diameter(cm)` == "DEAD"] <- "NA"
 
 View(tree_diameter1)
 
-usethis::use_data(plot_data01, overwrite = TRUE)
-
-
 #Plot Data 2
 
 #Creating year and height column 
@@ -65,9 +62,8 @@ usethis::use_data(tree_diameter1, overwrite = TRUE)
 usethis::use_data(tree_diameter2, overwrite = TRUE)
 
 #Run this in console for documentation functionality 
-#When ran together with rest of data, causes R to run without stop? Troubleshoot?
 devtools::document()
 
 #Documentation complete:
-#Use plot_data01 and ?plot_data01 to see plot data01 documentation
-#Use plot_data02 and ?plot_data02 to see plot data02 documentation
+#Use tree_diameter1 and ?tree_diameter1 to see plot data01 documentation
+#Use tree_diameter2 and ?tree_diameter2 to see plot data02 documentation

### 2021-06-29 R/data.R
Added .Renviron to update R, fixed error in description, updated documentation, fixed variable names and missing values in dataset

@@ -129,14 +129,15 @@
 #' @docType data
 #' @format 
 #' \describe{
-#'  \item{Module}{20 x 50 m and divided into 10 subplot modules of 110 m. There are five 10 x 10 modules along central 50 m axis.}
+#'  \item{Module}{Module number that represents one of the 10 subplot modules that are 110 m
+#'  and 20 x 50 m. There are five 10 x 10 modules along central 50 m axis.}
 #'  \item{Tag}{Tag numbers used to identify each tree.} 
 #'  \item{Species}{Tree species include Acer rubrum, Betula lenta, Betula papyrifera, Fagus grandifolia, Hamamelis virginiana, 
 #'  Pinus strobus, Quercus rubra, and Tsuga canadensis.}
 #'  \item{Position}{Stage of growth for each individual tree.}
 #'  \item{Year}{Data collected from 2010-2015 in the fall semesters.}
 #'  \item{Notes}{Notes collected on the wellbeing of tree species, including notes on death or poor health.}
-#'  \item{Diameter(cm)}{Tree diameter measured in centimeters and at 1.4 meters high above the ground.}
+#'  \item{Diameter}{Tree diameter measured in centimeters and at 1.4 meters high above the ground.}
 #'  \item{People}{Data obtained from Jesse Bellemare and Smith College students from BIO364-365 courses.}
 #' }
 "tree_diameter1"
@@ -148,13 +149,14 @@
 #' @docType data
 #' @format 
 #' \describe{
-#'  \item{Module}{20 x 50 m and divided into 10 subplot modules of 110 m. There are five 10 x 10 modules along central 50 m axis.}
+#'  \item{Module}{Module number that represents one of the 10 subplot modules that are 110 m
+#'  and 20 x 50 m. There are five 10 x 10 modules along central 50 m axis.}
 #'  \item{Tag}{Tag numbers used to identify each tree.}
 #'  \item{Species}{Tree species include Acer rubrum, Betula lenta, Fagus grandifolia, Pinus strobus, 
 #'  Quercus rubra, and Tsuga canadensis.}
 #'  \item{Year}{Data collected from 2009-2012 in the fall semesters.}
 #'  \item{Notes}{Notes collected on the wellbeing of tree species, including notes on death or poor health.}
-#'  \item{Diameter(cm)}{Tree diameter measured in centimeters and at 1.4 meters high above the ground.}
[…]

### 2021-06-29 data-raw/plot_data.R

@@ -14,23 +14,28 @@ tree_diameter2 <- read_excel("data-raw/MacLeish Data_Plot MC-02.xlsx")
 #Plot Data 1
 #Creating year and height column 
 tree_diameter1 <- tree_diameter1 %>%
-  pivot_longer(c(`Fall'15`, `Fall'14`,`Fall'13`,`Fall'12`,`Fall'11`,`Fall'10`), names_to = "Year", values_to = "Diameter(cm)")
+  pivot_longer(c(`Fall'15`, `Fall'14`,`Fall'13`,`Fall'12`,`Fall'11`,`Fall'10`), names_to = "year", values_to = "diameter")
 
 #Separating fall and year into new columns 
 tree_diameter1 <- tree_diameter1 %>%
-  separate(Year, c("Semester", "Year"), sep = 4)
+  separate(year, c("semester", "year"), sep = 4)
 
 #Changing abbreviated year into full year 
-tree_diameter1$Year[tree_diameter1$Year == "'15"] <- "2015"
-tree_diameter1$Year[tree_diameter1$Year == "'14"] <- "2014"
-tree_diameter1$Year[tree_diameter1$Year == "'13"] <- "2013"
-tree_diameter1$Year[tree_diameter1$Year == "'12"] <- "2012"
-tree_diameter1$Year[tree_diameter1$Year == "'11"] <- "2011"
-tree_diameter1$Year[tree_diameter1$Year == "'10"] <- "2010"
+tree_diameter1$year[tree_diameter1$year == "'15"] <- "2015"
+tree_diameter1$year[tree_diameter1$year == "'14"] <- "2014"
+tree_diameter1$year[tree_diameter1$year == "'13"] <- "2013"
+tree_diameter1$year[tree_diameter1$year == "'12"] <- "2012"
+tree_diameter1$year[tree_diameter1$year == "'11"] <- "2011"
+tree_diameter1$year[tree_diameter1$year == "'10"] <- "2010"
 
 #Changing value "DEAD" to NA for diameter
 #Tree diameter didn't increase or decrease over time 
-tree_diameter1$`Diameter(cm)`[tree_diameter1$`Diameter(cm)` == "DEAD"] <- "NA"
+tree_diameter1$`diameter`[tree_diameter1$`diameter` == "DEAD"] <- "NA"
+
+#Changing variable names to lowercase and removing numerical units 
+tree_diameter1 <- tree_diameter1 %>%
[…]

### 2021-07-06 R/data.R
Added seealso to tree_diameter

@@ -127,6 +127,7 @@
 #' for parasitic Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
 #' Tree diameter was measured at 1.4 meters high above the ground.
 #' @docType data
+#' @seealso [tree_diameter2]
 #' @format 
 #' \describe{
 #'  \item{Module}{Module number that represents one of the 10 subplot modules that are 110 m
@@ -147,6 +148,7 @@
 #' for parasitic Hemlock Woolly Adelgid dominated areas on the Western side of MacLeish. 
 #' Tree diameter was measured at 1.4 meters high above the ground.
 #' @docType data
+#' @seealso [tree_diameter1]
 #' @format 
 #' \describe{
 #'  \item{Module}{Module number that represents one of the 10 subplot modules that are 110 m

### 2021-07-06 R/data.R
Use roxygen2md to write all roxygen code using markdown format

@@ -5,18 +5,18 @@
 #'
 #' @details The Macleish Field Station is a remote outpost owned by Smith
 #' College and used for field research. There are two weather stations on the 
-#' premises. One is called \code{WhatelyMet} and the other is \code{OrchardMet}.
+#' premises. One is called `WhatelyMet` and the other is `OrchardMet`.
 #' 
-#' The \code{WhatelyMet} station is located at (42.448470, -72.680553) and
-#' the \code{OrchardMet} station is at (42.449653, -72.680315).
+#' The `WhatelyMet` station is located at (42.448470, -72.680553) and
+#' the `OrchardMet` station is at (42.449653, -72.680315).
 #' 
-#' \code{WhatelyMet} is located at the end of Poplar Hill Road in Whately, 
-#' Massachusetts, USA. The meteorological instruments of \code{WhatelyMet} (except the 
+#' `WhatelyMet` is located at the end of Poplar Hill Road in Whately, 
+#' Massachusetts, USA. The meteorological instruments of `WhatelyMet` (except the 
 #' rain gauge) are mounted at the top of a tower 25.3 m tall, well above the 
 #' surrounding forest canopy. The tower is located on a local ridge at an 
 #' elevation 250.75m above sea level.
 #' 
-#' \code{OrchardMet} is located about 250 m north of the first tower in an open 
+#' `OrchardMet` is located about 250 m north of the first tower in an open 
 #' field next to an apple orchard. Full canopy trees (~20 m tall) are within 
 #' 30 m of this station. This station has a standard instrument configuration 
 #' with temperature, relative humidity, solar radiation, and barometric 
@@ -26,18 +26,18 @@
 #' ground surface 2 m south of the tower. The tower is located 258.1 m above 
 #' sea level. Data collection at OrchardMet began on June 27th, 2014. 
 #' 
-#' The variables shown above are weather data collected at \code{WhatelyMet} and 
-#' \code{OrchardMet} during 2015. Solar radiation is measured in two different ways: 
-#' see \code{SlrW_Avg}or the \code{PAR} variables for Photosynthetic Active Radiation.
+#' The variables shown above are weather data collected at `WhatelyMet` and 
+#' `OrchardMet` during 2015. Solar radiation is measured in two different ways: 
+#' see `SlrW_Avg`or the `PAR` variables for Photosynthetic Active Radiation.
 #' 
[…]

### 2021-07-11 data-raw/plot_data.R
Fixed tree_diameter1 value name and added test graphs

@@ -31,7 +31,7 @@ tree_diameter1$year[tree_diameter1$year == "'11"] <- "2011"
 tree_diameter1$year[tree_diameter1$year == "'10"] <- "2010"
 
 # Changing value "DEAD" to NA for diameter
-# Tree diameter didn't increase or decrease over time 
+# Tree diameter didn't increase or decrease over time when dead
 tree_diameter1$`diameter`[tree_diameter1$`diameter` == "DEAD"] <- "NA"
 
 # Changing variable names to lowercase and removing numerical units 
@@ -42,6 +42,9 @@ tree_diameter1 <- tree_diameter1 %>%
 # Moved notes to final column
 tree_diameter1 <- tree_diameter1 %>% 
   select(module, tag, species, position, semester, year, diameter, notes)
+
+# Change value "sub-canopy" to "subcanopy"
+tree_diameter1$position[tree_diameter1$position == "sub-canopy"] <- "subcanopy"
 
 # Changing year and diameter from character to numeric variables 
 tree_diameter1$year <- as.numeric(tree_diameter1$year)

### 2021-07-14 tests/testgraphs.Rmd
Created new branch for test graphs, and adjusted year vs position bar graph

---
title: "Tree Graphs Test"
author: "Dominique Kelly"
date: "7/9/2021"
output: html_document
---

```{r setup, include=FALSE}
library(macleish)
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(forcats)
```

```{r}
head(tree_diameter1)
```

```{r}
p <- tree_diameter1 %>%
  ggplot( aes(x=diameter)) +
    geom_histogram( binwidth=1, fill="#69b3a2", color="#e9ecef") +
    scale_x_continuous(limits = c(0,60)) +
    scale_y_continuous(limits = c(0,100))
p
```

```{r}
q <- tree_diameter1 %>%
  ggplot( aes(x=diameter, color=species, fill=species)) +
  geom_histogram(binwidth=50, color="#e9ecef", alpha=0.6, position = 'identity') +
  scale_fill_viridis(discrete=TRUE) +
  scale_color_viridis(discrete=TRUE) +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
  #scale_x_continuous(limits = c(0,60)) +
  facet_grid(species~year, scales="free_y")
q
```

```{r}
x <- ggplot(tree_diameter1, aes(x = species)) +
  geom_bar(stat = "count") +
  theme(axis.text.x = element_text(angle = 60, hjust =1))
x
```

```{r}
y <- tree_diameter1 %>%
  ggplot(aes(x=year, y=diameter, fill=species)) +
  geom_bar(stat='identity', position='dodge', colour="black") +
  coord_flip() +
  scale_x_continuous(limits = c(2010,2015))
y
```

```{r}
z <- tree_diameter1 %>%
  ggplot(aes(x=position, y=diameter, fill=species)) +
  geom_bar(stat="identity", position="dodge") +
  scale_y_continuous(limits = c(0, 60))
z
#order of position - canopy, subcanopy, emergent, sapling 
#consider common names for species 
#add line graph for review
```

```{r}
w <- tree_diameter1 %>%
  ggplot( aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60))
w
```

```{r}
w2 <- tree_diameter1 %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Tsuga canadensis", "Quercus rubra"))
w2
```

```{r}
r <- tree_diameter2 %>%
  ggplot( aes(x=diameter, y=species)) +
  geom_boxplot() +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year)
r
```

# Any way to graph to focus on a specific year or plant species without butchering the data?

### 2021-07-14 data-raw/plot_data.R

@@ -1,0 +1,94 @@
+library(readxl)
+library(tidyverse)
+library(janitor)
+library(lubridate)
+library(stringr)
+library(usethis)
+library(devtools)
+library(dplyr)
+
+
+# Uploading data into R
+tree_diameter1 <- read_excel("data-raw/MacLeish Data_Plot MC-01.xlsx")
+tree_diameter2 <- read_excel("data-raw/MacLeish Data_Plot MC-02.xlsx")
+
+
+# Plot Data 1
+# Creating year and height column 
+tree_diameter1 <- tree_diameter1 %>%
+  pivot_longer(c(`Fall'15`, `Fall'14`,`Fall'13`,`Fall'12`,`Fall'11`,`Fall'10`), names_to = "year", values_to = "diameter")
+
+# Separating fall and year into new columns 
+tree_diameter1 <- tree_diameter1 %>%
+  separate(year, c("semester", "year"), sep = 4)
+
+# Changing abbreviated year into full year 
+tree_diameter1$year[tree_diameter1$year == "'15"] <- "2015"
+tree_diameter1$year[tree_diameter1$year == "'14"] <- "2014"
+tree_diameter1$year[tree_diameter1$year == "'13"] <- "2013"
+tree_diameter1$year[tree_diameter1$year == "'12"] <- "2012"
+tree_diameter1$year[tree_diameter1$year == "'11"] <- "2011"
+tree_diameter1$year[tree_diameter1$year == "'10"] <- "2010"
+
+# Changing value "DEAD" to NA for diameter
+# Tree diameter didn't increase or decrease over time when dead
+tree_diameter1$`diameter`[tree_diameter1$`diameter` == "DEAD"] <- "NA"
+
+# Changing variable names to lowercase and removing numerical units 
+tree_diameter1 <- tree_diameter1 %>%
+  rename(notes = `Notes:`, module = `Module#`, tag = `Tag#`) %>% 
+  rename_with(tolower) 
+
+# Moved notes to final column
+tree_diameter1 <- tree_diameter1 %>% 
+  select(module, tag, species, position, semester, year, diameter, notes)
+
+# Change value "sub-canopy" to "subcanopy"
+tree_diameter1$position[tree_diameter1$position == "sub-canopy"] <- "subcanopy"
+
+# Changing year and diameter from character to numeric variables 
+tree_diameter1$year <- as.numeric(tree_diameter1$year)
[…]

### 2021-07-14 tests/testgraphs.Rmd
Added common names for tree species and information about position

@@
 ```{r}
-y <- tree_diameter1 %>%
-  ggplot(aes(x=year, y=diameter, fill=species)) +
-  geom_bar(stat='identity', position='dodge', colour="black") +
-  coord_flip() +
-  scale_x_continuous(limits = c(2010,2015))
-y
-```
-
-```{r}
 z <- tree_diameter1 %>%
+  mutate(position = fct_relevel(position,
+                                "emergent", "canopy", "subcanopy", "sapling")) %>%
   ggplot(aes(x=position, y=diameter, fill=species)) +
@@
 
+```{r}
+t <- tree_diameter1 %>%
+  ggplot(aes(x=year, y=diameter, color=species)) +
+  geom_line() + 
+  geom_point()
+t
+```
+
 # Any way to graph to focus on a specific year or plant species without butchering the data?

### 2021-07-14 R/data.R

@@ -133,9 +133,10 @@
 #'  \item{Module}{Module number that represents one of the 10 subplot modules that are 110 m
 #'  and 20 x 50 m. There are five 10 x 10 modules along central 50 m axis.}
 #'  \item{Tag}{Tag numbers used to identify each tree.} 
-#'  \item{Species}{Tree species include Acer rubrum, Betula lenta, Betula papyrifera, Fagus grandifolia, Hamamelis virginiana, 
-#'  Pinus strobus, Quercus rubra, and Tsuga canadensis.}
-#'  \item{Position}{Stage of growth for each individual tree.}
+#'  \item{Species}{Tree species include Red Maple (Acer rubrum), Sweet Birch (Betula lenta), Paper Birch (Betula papyrifera), American Beech (Fagus grandifolia), 
+#'  American witch-hazel (Hamamelis virginiana), Eastern White Pine (Pinus strobus), Northern Red Oak (Quercus rubra), and Eastern Hemlock (Tsuga canadensis).}
+#'  \item{Position}{Stage of growth for each individual tree. The emergent position are the tallest trees, followed by canopy, subcanopy, 
+#'  and finally, sapling trees, which are the smallest trees.}
 #'  \item{Year}{Data collected from 2010-2015 in the fall semesters.}
 #'  \item{Notes}{Notes collected on the wellbeing of tree species, including notes on death or poor health.}
 #'  \item{Diameter}{Tree diameter measured in centimeters and at 1.4 meters high above the ground.}
@@ -154,8 +155,8 @@
 #'  \item{Module}{Module number that represents one of the 10 subplot modules that are 110 m
 #'  and 20 x 50 m. There are five 10 x 10 modules along central 50 m axis.}
 #'  \item{Tag}{Tag numbers used to identify each tree.}
-#'  \item{Species}{Tree species include Acer rubrum, Betula lenta, Fagus grandifolia, Pinus strobus, 
-#'  Quercus rubra, and Tsuga canadensis.}
+#'  \item{Species}{Tree species include Red Maple (Acer rubrum), Sweet Birch (Betula lenta), American Beech (Fagus grandifolia), Eastern White Pine (Pinus strobus), 
+#'  Northern Red Oak (Quercus rubra), and Eastern Hemlock (Tsuga canadensis).}
 #'  \item{Year}{Data collected from 2009-2012 in the fall semesters.}
[…]

### 2021-07-14 tests/testgraphs.Rmd
Added line graph for review

@@
 q
+#y-axis fluctates, consider adjustment 
 ```
@@
 z <- tree_diameter1 %>%
-  mutate(position = fct_relevel(position,
-                                "emergent", "canopy", "subcanopy", "sapling")) %>%
   ggplot(aes(x=position, y=diameter, fill=species)) +
@@
 z
-#order of position - canopy, subcanopy, emergent, sapling 
-#consider common names for species 
-#add line graph for review
 ```
@@
   scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
-  scale_x_continuous(limits=c(0,60))
+  scale_x_continuous(limits=c(0,60)) +
+  facet_wrap(~year)
 w
@@
 t <- tree_diameter1 %>%
-  ggplot(aes(x=year, y=diameter, color=species)) +
+  tail(10) %>%
+  ggplot(aes(x=year, y=diameter)) +
+  #when grouped by species, the graph only accounts for Tsuga canadensis
   geom_line() +

### 2021-07-14 data-raw/plot_data.R
Change species names from scientific to common names

@@ -50,6 +50,15 @@ tree_diameter1$position[tree_diameter1$position == "sub-canopy"] <- "subcanopy"
 tree_diameter1$year <- as.numeric(tree_diameter1$year)
 tree_diameter1$diameter <- as.numeric(tree_diameter1$diameter)
 
+# Changing species name from scientific to common name
+tree_diameter1$species[tree_diameter1$species == "Acer rubrum"] <- "Red Maple"
+tree_diameter1$species[tree_diameter1$species == "Betula lenta"] <- "Sweet Birch"
+tree_diameter1$species[tree_diameter1$species == "Betula papyrifera"] <- "Paper Birch"
+tree_diameter1$species[tree_diameter1$species == "Fagus grandifolia"] <- "American Beech"
+tree_diameter1$species[tree_diameter1$species == "Hamamelis virginiana"] <- "American witch-hazel"
+tree_diameter1$species[tree_diameter1$species == "Pinus strobus"] <- "Eastern White Pine"
+tree_diameter1$species[tree_diameter1$species == "Quercus rubra"] <- "Northern Red Oak"
+tree_diameter1$species[tree_diameter1$species == "Tsuga canadensis"] <- "Eastern Hemlock"
 
 # Plot Data 2
 # Creating year and height column 
@@ -88,6 +97,13 @@ tree_diameter2 <- tree_diameter2 %>%
 tree_diameter2$year <- as.numeric(tree_diameter2$year)
 tree_diameter2$diameter <- as.numeric(tree_diameter2$diameter)
 
+# Changing species name from scientific to common name
+tree_diameter2$species[tree_diameter2$species == "Acer rubrum"] <- "Red Maple"
+tree_diameter2$species[tree_diameter2$species == "Betula lenta"] <- "Sweet Birch"
+tree_diameter2$species[tree_diameter2$species == "Fagus grandifolia"] <- "American Beech"
+tree_diameter2$species[tree_diameter2$species == "Pinus strobus"] <- "Eastern White Pine"
+tree_diameter2$species[tree_diameter2$species == "Quercus rubra"] <- "Northern Red Oak"
+tree_diameter2$species[tree_diameter2$species == "Tsuga canadensis"] <- "Eastern Hemlock"
 
 # Write both to package
 usethis::use_data(tree_diameter1, overwrite = TRUE)

### 2021-07-14 data-raw/plot_data.R
Trivial change

@@ -55,7 +55,7 @@ tree_diameter1$species[tree_diameter1$species == "Acer rubrum"] <- "Red Maple"
 tree_diameter1$species[tree_diameter1$species == "Betula lenta"] <- "Sweet Birch"
 tree_diameter1$species[tree_diameter1$species == "Betula papyrifera"] <- "Paper Birch"
 tree_diameter1$species[tree_diameter1$species == "Fagus grandifolia"] <- "American Beech"
-tree_diameter1$species[tree_diameter1$species == "Hamamelis virginiana"] <- "American witch-hazel"
+tree_diameter1$species[tree_diameter1$species == "Hamamelis virginiana"] <- "American Witch-hazel"
 tree_diameter1$species[tree_diameter1$species == "Pinus strobus"] <- "Eastern White Pine"
 tree_diameter1$species[tree_diameter1$species == "Quercus rubra"] <- "Northern Red Oak"
 tree_diameter1$species[tree_diameter1$species == "Tsuga canadensis"] <- "Eastern Hemlock"

### 2021-07-14 tests/testgraphs.Rmd
Trivial change

@@
   scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
-  scale_y_discrete(limits=c("Tsuga canadensis", "Quercus rubra"))
+  scale_y_discrete(limits=c("Eastern Hemlock"))
 w2

### 2021-07-14 tests/testgraphs.Rmd
Added reorder of position for bar graph

@@
 z <- tree_diameter1 %>%
+  mutate(position = fct_relevel(position,
+                            "emergent", "canopy", "subcanopy", "sapling")) %>%
   ggplot(aes(x=position, y=diameter, fill=species)) +
@@
   geom_boxplot() +
+  coord_flip() +
   scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +

### 2021-07-15 data-raw/plot_data.R
Changed scientific names to species names

@@ -50,6 +50,15 @@ tree_diameter1$position[tree_diameter1$position == "sub-canopy"] <- "subcanopy"
 tree_diameter1$year <- as.numeric(tree_diameter1$year)
 tree_diameter1$diameter <- as.numeric(tree_diameter1$diameter)
 
+# Changing species name from scientific to common name
+tree_diameter1$species[tree_diameter1$species == "Acer rubrum"] <- "Red Maple"
+tree_diameter1$species[tree_diameter1$species == "Betula lenta"] <- "Sweet Birch"
+tree_diameter1$species[tree_diameter1$species == "Betula papyrifera"] <- "Paper Birch"
+tree_diameter1$species[tree_diameter1$species == "Fagus grandifolia"] <- "American Beech"
+tree_diameter1$species[tree_diameter1$species == "Hamamelis virginiana"] <- "American Witch-hazel"
+tree_diameter1$species[tree_diameter1$species == "Pinus strobus"] <- "Eastern White Pine"
+tree_diameter1$species[tree_diameter1$species == "Quercus rubra"] <- "Northern Red Oak"
+tree_diameter1$species[tree_diameter1$species == "Tsuga canadensis"] <- "Eastern Hemlock"
 
 # Plot Data 2
 # Creating year and height column 
@@ -88,6 +97,13 @@ tree_diameter2 <- tree_diameter2 %>%
 tree_diameter2$year <- as.numeric(tree_diameter2$year)
 tree_diameter2$diameter <- as.numeric(tree_diameter2$diameter)
 
+# Changing species name from scientific to common name
+tree_diameter2$species[tree_diameter2$species == "Acer rubrum"] <- "Red Maple"
+tree_diameter2$species[tree_diameter2$species == "Betula lenta"] <- "Sweet Birch"
+tree_diameter2$species[tree_diameter2$species == "Fagus grandifolia"] <- "American Beech"
+tree_diameter2$species[tree_diameter2$species == "Pinus strobus"] <- "Eastern White Pine"
+tree_diameter2$species[tree_diameter2$species == "Quercus rubra"] <- "Northern Red Oak"
+tree_diameter2$species[tree_diameter2$species == "Tsuga canadensis"] <- "Eastern Hemlock"
 
 # Write both to package
 usethis::use_data(tree_diameter1, overwrite = TRUE)

### 2021-07-16 tests/testgraphs.Rmd
trivial change

--- 2021-07-14 tests/testgraphs.Rmd
@@
 q
-#y-axis fluctates, consider adjustment 
 ```
@@
 z <- tree_diameter1 %>%
+  mutate(position = fct_relevel(position,
+                                "emergent", "canopy", "subcanopy", "sapling")) %>%
   ggplot(aes(x=position, y=diameter, fill=species)) +
@@
 z
+#order of position - canopy, subcanopy, emergent, sapling 
+#consider common names for species 
+#add line graph for review
 ```
@@
   scale_x_continuous(limits=c(0,60)) +
-  facet_wrap(~year)
+  facet_wrap(~year) +
+  labs(x = "Diameter (cm)", y = "Species", fill = "Position", title = "Distribution of Diameter based on Different Species at Different Positions Between 2010-2015")
 w
@@
   scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
-  scale_y_discrete(limits=c("Eastern Hemlock"))
+  scale_y_discrete(limits=c("Eastern Hemlock")) +
+  coord_flip() +
+  labs(x = "Diameter (cm)", y = "Species", fill = "Position", title = "Distribution of Diameter for Eastern Hemlock at Different Positions Between 2010-2015")
 w2
@@
   scale_x_continuous(limits=c(0,60)) +
-  facet_wrap(~year)
+  facet_wrap(~year) +
+  labs(x = "Diameter (cm)", y = "Species", title = "Distribution of Diameter based on Different Species Between 2009-2016")
 r
@@
 t <- tree_diameter1 %>%
-  tail(10) %>%
-  ggplot(aes(x=year, y=diameter)) +
-  #when grouped by species, the graph only accounts for Tsuga canadensis
+  ggplot(aes(x=year, y=diameter, color=species)) +
   geom_line() + 

### 2021-07-19 README.Rmd
Trivial change

@@
   )
+
 ```

### 2021-08-05 revdep/library.noindex/macleish/old/macleish/doc/macleish.Rmd
prep version bump

---
title: "Ada & Archibald MacLeish Field Station Data"
author: "Ben Baumer, Rose Goueth, Wencong Li (Priscilla) and Weijia Zhang (Vega), Paul Wetzel"
date: "2016-04-10"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using MacLeish Weather Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(knitr)
opts_chunk$set(fig.width = 6, fig.height = 4)
```

## MacLeish

The [`macleish`](http://www.github.com/beanumber/macleish) package for R contains weather data collected at the [Ada & Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php) in Whately, MA, as well as spatial data detailing various features of the property. This vignette will illustrate how these data can be used.

### Getting started:
To start using the package, load the `macleish` package into your R session:

```{r, message=FALSE}
library(macleish)
```

## Using the MacLeish Field Station weather data

Two data frames are included in the package: `whately_2015` and `orchard_2015`. These contain weather data averaged over every ten minute period for the calendar year 2015. The `head` and `tail` will give you the first (last) 6 readings from the whately weather station from 2015, respectively.

```{r}
head(whately_2015)
tail(whately_2015)
```

```{r, eval=FALSE}
head(orchard_2015)
tail(orchard_2015)
```

To access data during wider time spans, make use of the [`etl` framework](http://www.github.com/beanumber/etl) to download the data and import it into a database. Please see the documentation for `etl_extract` for further details and examples.

```{r, eval=FALSE}
help("etl_extract.etl_macleish")
```

## The 2015 MacLeish weather report

This portion of the vignette is largely a re-creation of the Macleish Field Station 2015 Weather Report.

#### Introduction to MacLeish Weather Stations

Weather conditions at Smith College's [Ada & Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php) are recorded at the **WhatelyMet** weather station. This weather collection site is located at the end of Poplar Hill Road in Whately, Massachusetts, USA (Latitude 42 deg. 26 min. 56 sec. N Longitude 72 deg. 40 min. 50 sec. W). The meteorological instruments of WhatelyMet (except the rain gauge) are mounted at the top of a tower 25.3 m tall, well above the surrounding forest canopy. The tower is located on a local ridge at an elevation 250.75m above sea level.

![MacLeish Field Station](../inst/extdata/macleish_600px.jpg)

The second weather data collection site, known as **OrchardMet**, is located about 250 m north of the first tower in an open field next to an apple orchard. Full canopy trees (~20 m tall) are within 30 m of this station. This station has a standard instrument configuration with temperature, relative humidity, solar radiation, and barometric pressure measured between 1.5 and 2.0 m above the ground. Wind speed and direction are measured on a 10 m tall tower and precipitation is measured on the ground. Ground temperature is measured at 15 and 30 cm below the ground surface 2 m south of the tower. The tower is located 258.1 m above sea level. Data collection at OrchardMet began on June 27th, 2014.

This documentation describes the weather data collected at WhatelyMet and OrchardMet during 2015. It provides highlights of the year's weather as well as general trends that were observed. We hope that you find the documentation both interesting and useful. All data reported in this document are available through the [`macleish`](http://www.github.com/beanumber/macleish) package for R.

### Variables used in this documentation:

* `when`: Timestamp for each measurement set
* `temperature`: Average temperature (°C)
* `wind_speed`: Average windspeed (m/s)
* `wind_dir`: Wind direction (degree)
* `rel_humidty`: Relative Humidity (mm)
* `pressure`: Average atmospheric pressure (mb)
* `rainfall`: Main Rainfall amount per day (mm)
* `solar_radiation`: WhatelyMet Average Solar Radiance (W/m^2)
* `par_density`: OrchardMet Photosynthetically Active Radiation (sunlight between 400 and 700 nm) in average density (W/m^2)
* `par_total`: OrchardMet Photosynthetically Active Radiation (sunlight between 400 and 700 nm) in average total over measurement period (W/m^2)

### Air Temperature

In this example we visualize the trend of average daily temperature at the MacLeish Field Station over 2015.

```{r daily, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(lubridate)
daily <- whately_2015 %>%
  mutate(the_date = as.Date(when, tz = "EST")) %>%
  group_by(the_date) %>%
  summarize(
    N = n(), avg_temp = mean(temperature),
    max_temp = max(temperature),
    min_temp = min(temperature)
  )
```

```{r temp-plot, message=FALSE}
temp_plot <- ggplot(data = whately_2015, aes(x = when, y = temperature)) +
  geom_line(color = "lightgray") +
  geom_line(data = daily, aes(
    x = as.POSIXct(the_date),
    y = avg_temp
  )) +
  xlab(NULL) +
  ylab("Temperature (Celsius)")

if (require(mgcv)) {
  temp_plot + geom_smooth()
} else {
  temp_plot
}
```

As shown in the table below, the monthly average temperature in 2015 ranged from -6.4 °C in January to 21.6°C in July. The large difference in recorded temperatures between the two stations in November was the result of a loose wire that resulted in erroneous temperature readings at the OrchardMet station (see below).

```{r temp-table}
monthly_w <- whately_2015 %>%
  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
  group_by(the_month) %>%
  summarize(avg_temp = mean(temperature))
monthly_o <- orchard_2015 %>%
  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
  group_by(the_month) %>%
  summarize(avg_temp = mean(temperature))
monthly_w %>%
  inner_join(monthly_o, by = "the_month")
```

The highest recorded temperature at WhatelyMet was 33.08 °C on September 8th. The lowest recorded temperature was -22.28 °C on January 8th.

```{r temp-extremes}
whately_2015 %>%
  arrange(desc(temperature)) %>%
  head(1)
whately_2015 %>%
  arrange(temperature) %>%
  head(1)
```

The average daily temperature range recorded from both stations (daily maximum-minimum) was 10.4 °C. The maximum daily temperature range was 21.1 °C on May 8th at WhatelyMet.

```{r}
daily <- daily %>%
  mutate(temp_range = max_temp - min_temp)
daily %>%
  select(temp_range) %>%
  summary()
```

The minimum daily temperature range was 2.1 °C and occurred on April 9th at WhatelyMet. However, daily temperature ranges of less than three degrees also occurred on April 7th, February 9th, June 1st, June 28th.

```{r}
daily %>%
  arrange(desc(temp_range)) %>%
  head(1)
daily %>%
  arrange(temp_range) %>%
  head()
```

#### Anomalies

In late November, a loose wire in the OrchardMet station resulted in some erroneous temperature readings. We have left these readings in, but you should exercise caution when summarizing data that includes this time period. Imputation of these data would be a terrific exercise.

```{r orchard-anolomies}
orchard_2015 %>%
  filter(month(when) == 11) %>%
  ggplot(aes(x = when, y = temperature)) +
  geom_line()
```

### Relative Humidity

Percent average monthly relative humidity ranged from 56.4% (March) to 94% (December). Interestingly, WhatelyMet relative humidity values were notably higher than OrchardMet values starting in August. It is unclear why this pattern occurred during the last part of the year.

```{r humidity-table}
monthly_w <- whately_2015 %>%
  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
  group_by(the_month) %>%
  summarize(avg_humidity_w = mean(rel_humidity))
monthly_o <- orchard_2015 %>%
  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
  group_by(the_month) %>%
  summarize(avg_humidity_o = mean(rel_humidity))
monthly_w %>%
  inner_join(monthly_o, by = "the_month")
```

### Wind

Wind speed and direction is measured every second and then averaged and logged every 10 minutes at both weather stations. OrchardMet measures wind midway up the forest canopy (10 m high) in a small woodland clearing while WhatelyMet measures wind 25.3 m above the ground which is above the tree canopy.

OrchardMet is located in a woodland clearing where winds are buffeted by trees of the forest canopy. Most wind comes from the west and southwest, with 67% of the time less than 1 m/s. Wind speeds did not average over 3 m/s at any time of the year.

```{r, message=FALSE, warning=FALSE}
require(clifro)
orchard_2015 %>%
  with(windrose(wind_speed, wind_dir))
```

WhatelyMet is above the forest canopy and recorded winds frequently from the northwest, north, and south during the year. Average wind velocities were higher, with 46% of the measurements falling between 1 and 2 m/s, with maximum average velocities up to 6 m/s.

```{r, message=FALSE}
whately_2015 %>%
  with(windrose(wind_speed, wind_dir))
```

### Precipitation

A total of 1306 mm of precipitation was recorded at WhatelyMet during 2015.

```{r}
whately_2015 %>%
  summarize(total_rainfall = sum(rainfall))
```

Although precipitation is relatively evenly distributed across the year, precipitation totals were highest in June and lowest in May.

```{r rain-table}
monthly_w <- whately_2015 %>%
  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
  group_by(the_month) %>%
  summarize(total_precip_w = sum(rainfall))
monthly_o <- orchard_2015 %>%
  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
  group_by(the_month) %>%
  summarize(total_precip_o = sum(rainfall))
monthly_w %>%
  inner_join(monthly_o, by = "the_month")
```

Since the data was recorded every ten minutes, we need to group the data daily in order to get the mean rainfall amount per day.

```{r, message=FALSE}
daily_precip <- whately_2015 %>%
  mutate(the_date = as.Date(when, tz = "EST")) %>%
  group_by(the_date) %>%
  summarize(N = n(), total_precip = sum(rainfall)) %>%
  mutate(
    cum_precip = cumsum(total_precip),
    cum_rescale = (cum_precip / max(cum_precip)) * max(total_precip)
  )
```

The following plot will show you how much rainfall you would have per day at macleish field station over 2015, as well as the cumulative amount of rainfall over the course of the year.

```{r daily-precip, message=FALSE}
ggplot(
  data = daily_precip,
  aes(x = the_date, y = total_precip)
) +
  geom_bar(stat = "identity") +
  geom_line(aes(y = cum_rescale), color = "blue") +
  ylab("Daily Precipitation (mm)") +
  xlab(NULL)
```

February and March had the greatest number of precipitation events. Annual precipitation accumulated at a low, but fairly steady rate through June. After June rainfall levels increased and total accumulation increased sharply to the end of the calendar year. Starting in June a series of large rainfall events (40-50 mm) occurred regularly over the summer. The largest precipitation event in 2015 occurred on September 30th when 113.8 mm (8.7% of the annual total) of precipitation fell. During 2015, there were 15, 25.4 mm (1”) precipitation events; 2, 50.8 mm (2”) precipitation events; and 1, 76.2 mm (3”) precipitation event.

## Using the Macleish Field Station Geographic Data

### Maps

We can create a map of MacLeish using the `leaflet` package and the spatial data in the `macleish_layers` object. This is a `list` of `Spatial*DataFrame` objects that contain various pieces of information about the field station, including the location of buildings, streams, trails, and landmarks.

```{r}
names(macleish_layers)
```

These layers can be combined to provide a fuller picture of the activity at the Field Station.

```{r, eval=FALSE, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]],
    weight = 1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]],
    weight = 1
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)),
    popup = ~Label
  )
```

### 2021-08-05 revdep/checks.noindex/mdsr/old/mdsr.Rcheck/mdsr-Ex.R

@@ -1,0 +1,446 @@
+pkgname <- "mdsr"
+source(file.path(R.home("share"), "R", "examples-header.R"))
+options(warn = 1)
+library('mdsr')
+
+base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
+base::assign(".old_wd", base::getwd(), pos = 'CheckExEnv')
+cleanEx()
+nameEx("CIACountries")
+### * CIACountries
+
+flush(stderr()); flush(stdout())
+
+### Name: CIACountries
+### Title: Several variables on countries from the CIA Factbook, 2014.
+### Aliases: CIACountries
+### Keywords: datasets
+
+### ** Examples
+
+str(CIACountries)
+
+
+
+
+cleanEx()
+nameEx("Cherry")
+### * Cherry
+
+flush(stderr()); flush(stdout())
+
+### Name: Cherry
+### Title: Cherry Blossom runs
+### Aliases: Cherry
+### Keywords: datasets
+
+### ** Examples
+
+if (require(dplyr)) {
+  Cherry %>%
+    group_by(name.yob) %>%
+    count() %>%
+    group_by(n) %>%
+    count(name = "appearances")
+}
+
+
+
+cleanEx()
+nameEx("CholeraDeaths")
+### * CholeraDeaths
+
+flush(stderr()); flush(stdout())
+
+### Name: CholeraDeaths
+### Title: Deaths and Pumps from 1854 London cholera outbreak
+### Aliases: CholeraDeaths CholeraPumps
+### Keywords: datasets
+
+### ** Examples
+
+if (require(sf)) {
+  plot(st_geometry(CholeraDeaths))
+}
+
+
+
+cleanEx()
+nameEx("DataSciencePapers")
+### * DataSciencePapers
+
+flush(stderr()); flush(stdout())
+
+### Name: DataSciencePapers
+### Title: Data Science Papers from arXiv.org
+### Aliases: DataSciencePapers
+### Keywords: datasets
+
+### ** Examples
+
+
+data(DataSciencePapers)
+str(DataSciencePapers)
+
+
+
+
+cleanEx()
+nameEx("Emails_train")
+### * Emails_train
+
+flush(stderr()); flush(stdout())
+
+### Name: Emails_train
+### Title: Email Train
+### Aliases: Emails_train Emails_test
+### Keywords: datasets
+
+### ** Examples
+
+nrow(Emails_train)
+nrow(Emails_test)
+
+
[…]

### 2021-08-05 revdep/checks.noindex/mdsr/old/mdsr.Rcheck/tests/testthat/tests.R

@@ -1,0 +1,44 @@
+context("mdsr")
+
+test_that("scidb works", {
+  x <- dbConnect_scidb("airlines")
+  expect_s4_class(x, "DBIObject")
+  expect_output(print(x), "MySQLConnection")
+  
+  suppressWarnings(y <- tbl(x, "airports"))
+  expect_s3_class(y, c("tbl_dbi", "tbl_sql", "tbl"))
+  expect_match(DBI::dbGetInfo(x)$host, "^mdsr.+rds\\.amazonaws\\.com$")
+  expect_equal(DBI::dbGetInfo(x)$user, "mdsr_public")
+  expect_equal(
+    y %>% 
+      head(1) %>%
+      collect() %>%
+      nrow() %>%
+      suppressWarnings(), 
+    1
+  )
+  expect_length(DBI::dbListTables(x), 4)
+})
+
+test_that("download functions work", {
+  skip_on_cran()
+  BabynameDist <- make_babynames_dist()
+  expect_is(BabynameDist, "tbl_df")
+  
+  NCI60 <- etl_NCI60()
+  expect_is(NCI60, "tbl_df")
+  expect_equal(nrow(NCI60), 41078)
+})
+
+
+test_that("save_webshot works", {
+  skip_on_cran()
+  if (require(leaflet)) {
+    x <- leaflet() %>%
+      addTiles() %>%
+      addMarkers(lng = 174.768, lat = -36.852, popup = "The birthplace of R")
+    png <- save_webshot(x, tempfile())
+    expect_is(png, "fs_path")
+#    expect_true(file.exists(png))
+  }
+})

### 2021-08-05 revdep/library.noindex/macleish/old/macleish/doc/macleish.R

@@ -1,0 +1,165 @@
+## ---- include=FALSE-----------------------------------------------------------
+library(knitr)
+opts_chunk$set(fig.width = 6, fig.height = 4)
+
+## ---- message=FALSE-----------------------------------------------------------
+library(macleish)
+
+## -----------------------------------------------------------------------------
+head(whately_2015)
+tail(whately_2015)
+
+## ---- eval=FALSE--------------------------------------------------------------
+#  head(orchard_2015)
+#  tail(orchard_2015)
+
+## ---- eval=FALSE--------------------------------------------------------------
+#  help("etl_extract.etl_macleish")
+
+## ----daily, message=FALSE, warning=FALSE--------------------------------------
+library(ggplot2)
+library(dplyr)
+library(lubridate)
+daily <- whately_2015 %>%
+  mutate(the_date = as.Date(when, tz = "EST")) %>%
+  group_by(the_date) %>%
+  summarize(
+    N = n(), avg_temp = mean(temperature),
+    max_temp = max(temperature),
+    min_temp = min(temperature)
+  )
+
+## ----temp-plot, message=FALSE-------------------------------------------------
+temp_plot <- ggplot(data = whately_2015, aes(x = when, y = temperature)) +
+  geom_line(color = "lightgray") +
+  geom_line(data = daily, aes(
+    x = as.POSIXct(the_date),
+    y = avg_temp
+  )) +
+  xlab(NULL) +
+  ylab("Temperature (Celsius)")
+
+if (require(mgcv)) {
+  temp_plot + geom_smooth()
+} else {
+  temp_plot
+}
+
+## ----temp-table---------------------------------------------------------------
+monthly_w <- whately_2015 %>%
+  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
+  group_by(the_month) %>%
+  summarize(avg_temp = mean(temperature))
+monthly_o <- orchard_2015 %>%
+  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
+  group_by(the_month) %>%
+  summarize(avg_temp = mean(temperature))
+monthly_w %>%
+  inner_join(monthly_o, by = "the_month")
+
+## ----temp-extremes------------------------------------------------------------
+whately_2015 %>%
+  arrange(desc(temperature)) %>%
+  head(1)
+whately_2015 %>%
+  arrange(temperature) %>%
+  head(1)
+
[…]

### 2021-08-05 rhub.R

@@ -5,5 +5,6 @@ devtools::check_rhub(
   interactive = FALSE,
   platforms = rhub::platforms() %>%
     filter(!is.na(`cran-name`)) %>%
-    pull(name)
+    pull(name),
+  env_vars=c(R_COMPILE_AND_INSTALL_PACKAGES = "always")
 )

### 2021-08-06 README.Rmd
Update all stale URL's

@@
 
-# macleish <img src='man/figures/logo.png' align="right" height="139" />
+# macleish <img src='man/figures/logo.png' align="right" height="139"/>
 
 [![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
-[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)
 
-The [Ada and Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
+The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
 
@@
 
-This R package allows you to download and process weather data using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station.
+This R package allows you to download and process weather data using the [ETL](https://www.github.com/beanumber/etl) framework from the MacLeish Field Station.
 It also contains shapefiles for contextualizing spatial information.
@@
 Weather readings are logged every 10 minutes.
-Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](http://www.github.com/beanumber/etl) framework.
+Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](https://www.github.com/beanumber/etl) framework.
 Please see the documentation for that package for more information about how this works.
@@
 
-- [Ada and Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php)
+- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
 - **[etl](https://www.github.com/beanumber/etl)**

### 2021-08-06 R/data.R

@@ -52,7 +52,7 @@
 #'   \item{par_density}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average density of Watts/meters^2. One of two solar measurements for Orchard}
 #'   \item{par_total}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average total over measurement period of Watts/meters^2. One of two solar measurements for Orchard}
 #' }
-#' @source These data are recorded at <http://www.smith.edu/ceeds/macleish_monitoring.php> 
+#' @source These data are recorded at <https://www.smith.edu/about-smith/sustainable-smith/ceeds> 
 "whately_2015"
 
 #' @rdname whately_2015

### 2021-08-06 R/mass_gis.R

@@ -8,7 +8,7 @@
 #' transform the projection to EPSG:4326, compute their intersection with the
 #' boundary of the MacLeish property, and return the resulting 
 #' [sf::sf()] object. 
-#' @source http://www.mass.gov/anf/research-and-tech/it-serv-and-support/application-serv/office-of-geographic-information-massgis/datalayers/layerlist.html
+#' @source https://www.mass.gov/info-details/massgis-data-layers
 #' @export
 #' @examples 
 #' 

### 2021-08-06 revdep/checks.noindex/mdsr/new/mdsr.Rcheck/tests/testthat.R
Remove revdep

@@ -1,4 +1,0 @@
-library(testthat)
-library(mdsr)
-
-test_check("mdsr")

### 2021-08-06 revdep/checks.noindex/mdsr/old/mdsr.Rcheck/mdsr-Ex.R

@@ -1,446 +1,0 @@
-pkgname <- "mdsr"
-source(file.path(R.home("share"), "R", "examples-header.R"))
-options(warn = 1)
-library('mdsr')
-
-base::assign(".oldSearch", base::search(), pos = 'CheckExEnv')
-base::assign(".old_wd", base::getwd(), pos = 'CheckExEnv')
-cleanEx()
-nameEx("CIACountries")
-### * CIACountries
-
-flush(stderr()); flush(stdout())
-
-### Name: CIACountries
-### Title: Several variables on countries from the CIA Factbook, 2014.
-### Aliases: CIACountries
-### Keywords: datasets
-
-### ** Examples
-
-str(CIACountries)
-
-
-
-
-cleanEx()
-nameEx("Cherry")
-### * Cherry
-
-flush(stderr()); flush(stdout())
-
-### Name: Cherry
-### Title: Cherry Blossom runs
-### Aliases: Cherry
-### Keywords: datasets
-
-### ** Examples
-
-if (require(dplyr)) {
-  Cherry %>%
-    group_by(name.yob) %>%
-    count() %>%
-    group_by(n) %>%
-    count(name = "appearances")
-}
-
-
-
-cleanEx()
-nameEx("CholeraDeaths")
-### * CholeraDeaths
-
-flush(stderr()); flush(stdout())
-
-### Name: CholeraDeaths
-### Title: Deaths and Pumps from 1854 London cholera outbreak
-### Aliases: CholeraDeaths CholeraPumps
-### Keywords: datasets
-
-### ** Examples
-
-if (require(sf)) {
-  plot(st_geometry(CholeraDeaths))
-}
-
-
-
-cleanEx()
-nameEx("DataSciencePapers")
-### * DataSciencePapers
-
-flush(stderr()); flush(stdout())
-
-### Name: DataSciencePapers
-### Title: Data Science Papers from arXiv.org
-### Aliases: DataSciencePapers
-### Keywords: datasets
-
-### ** Examples
-
-
-data(DataSciencePapers)
-str(DataSciencePapers)
-
-
-
-
-cleanEx()
-nameEx("Emails_train")
-### * Emails_train
-
-flush(stderr()); flush(stdout())
-
-### Name: Emails_train
-### Title: Email Train
-### Aliases: Emails_train Emails_test
-### Keywords: datasets
-
-### ** Examples
-
-nrow(Emails_train)
-nrow(Emails_test)
-
-
-
[…]

### 2021-08-06 revdep/checks.noindex/mdsr/old/mdsr.Rcheck/tests/testthat/tests.R

@@ -1,44 +1,0 @@
-context("mdsr")
-
-test_that("scidb works", {
-  x <- dbConnect_scidb("airlines")
-  expect_s4_class(x, "DBIObject")
-  expect_output(print(x), "MySQLConnection")
-  
-  suppressWarnings(y <- tbl(x, "airports"))
-  expect_s3_class(y, c("tbl_dbi", "tbl_sql", "tbl"))
-  expect_match(DBI::dbGetInfo(x)$host, "^mdsr.+rds\\.amazonaws\\.com$")
-  expect_equal(DBI::dbGetInfo(x)$user, "mdsr_public")
-  expect_equal(
-    y %>% 
-      head(1) %>%
-      collect() %>%
-      nrow() %>%
-      suppressWarnings(), 
-    1
-  )
-  expect_length(DBI::dbListTables(x), 4)
-})
-
-test_that("download functions work", {
-  skip_on_cran()
-  BabynameDist <- make_babynames_dist()
-  expect_is(BabynameDist, "tbl_df")
-  
-  NCI60 <- etl_NCI60()
-  expect_is(NCI60, "tbl_df")
-  expect_equal(nrow(NCI60), 41078)
-})
-
-
-test_that("save_webshot works", {
-  skip_on_cran()
-  if (require(leaflet)) {
-    x <- leaflet() %>%
-      addTiles() %>%
-      addMarkers(lng = 174.768, lat = -36.852, popup = "The birthplace of R")
-    png <- save_webshot(x, tempfile())
-    expect_is(png, "fs_path")
-#    expect_true(file.exists(png))
-  }
-})

### 2021-08-06 revdep/library.noindex/macleish/old/macleish/doc/macleish.R

@@ -1,165 +1,0 @@
-## ---- include=FALSE-----------------------------------------------------------
-library(knitr)
-opts_chunk$set(fig.width = 6, fig.height = 4)
-
-## ---- message=FALSE-----------------------------------------------------------
-library(macleish)
-
-## -----------------------------------------------------------------------------
-head(whately_2015)
-tail(whately_2015)
-
-## ---- eval=FALSE--------------------------------------------------------------
-#  head(orchard_2015)
-#  tail(orchard_2015)
-
-## ---- eval=FALSE--------------------------------------------------------------
-#  help("etl_extract.etl_macleish")
-
-## ----daily, message=FALSE, warning=FALSE--------------------------------------
-library(ggplot2)
-library(dplyr)
-library(lubridate)
-daily <- whately_2015 %>%
-  mutate(the_date = as.Date(when, tz = "EST")) %>%
-  group_by(the_date) %>%
-  summarize(
-    N = n(), avg_temp = mean(temperature),
-    max_temp = max(temperature),
-    min_temp = min(temperature)
-  )
-
-## ----temp-plot, message=FALSE-------------------------------------------------
-temp_plot <- ggplot(data = whately_2015, aes(x = when, y = temperature)) +
-  geom_line(color = "lightgray") +
-  geom_line(data = daily, aes(
-    x = as.POSIXct(the_date),
-    y = avg_temp
-  )) +
-  xlab(NULL) +
-  ylab("Temperature (Celsius)")
-
-if (require(mgcv)) {
-  temp_plot + geom_smooth()
-} else {
-  temp_plot
-}
-
-## ----temp-table---------------------------------------------------------------
-monthly_w <- whately_2015 %>%
-  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
-  group_by(the_month) %>%
-  summarize(avg_temp = mean(temperature))
-monthly_o <- orchard_2015 %>%
-  mutate(the_month = month(when, label = TRUE, abbr = FALSE)) %>%
-  group_by(the_month) %>%
-  summarize(avg_temp = mean(temperature))
-monthly_w %>%
-  inner_join(monthly_o, by = "the_month")
-
-## ----temp-extremes------------------------------------------------------------
-whately_2015 %>%
-  arrange(desc(temperature)) %>%
-  head(1)
-whately_2015 %>%
-  arrange(temperature) %>%
-  head(1)
-
[…]

### 2021-08-06 README.Rmd
More URL fixes

@@
 
-This R package allows you to download and process weather data using the [ETL](https://www.github.com/beanumber/etl) framework from the MacLeish Field Station.
+This R package allows you to download and process weather data using the [ETL](https://github.com/beanumber/etl) framework from the MacLeish Field Station.
 It also contains shapefiles for contextualizing spatial information.
@@
 Weather readings are logged every 10 minutes.
-Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](https://www.github.com/beanumber/etl) framework.
+Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](https://github.com/beanumber/etl) framework.
 Please see the documentation for that package for more information about how this works.
@@
 - [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
-- **[etl](https://www.github.com/beanumber/etl)**
+- **[etl](https://github.com/beanumber/etl)**

### 2022-06-06 README.Rmd
added lifecycle badge

@@
 
+<!-- badges: start -->
 [![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
-[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)  [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
+<!-- badges: end -->
 

### 2022-06-06 joss_paper/paper.Rmd
reorganize paper files

---
title: 'The MacLeish Package: R Package for analyzing weather and spatial data'
date: "`r Sys.Date()`"
authors:
  - name: Benjamin S. Baumer
    orcid: 0000-0002-3279-0516
    affiliation: 1
  - name: Dominique Kelly
    orcid: 0000-0001-7186-9385
    affiliation: 1
  - name: Albert Y. Kim
    orcid: 0000-0001-7824-306X
    affiliation: 1
affiliations: 
 - name: Smith College, Northampton, Massachusetts, USA  
   index: 1
bibliography: refs.bib
biblio-style: apa
tags:
  - R
  - forest
  - farmland
  - weather
  - spatial analysis 
output:
  rticles::joss_article:
    keep_md: yes
    number_sections: yes
---

```{r, echo=FALSE, results = FALSE, warning=FALSE, message=FALSE}
# knitr settings
knitr::opts_chunk$set(
  # Code output:
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  # Figure:
  out.width = "100%",
  fig.width = 16 / 2.5,
  fig.height = 9 / 2.5,
  fig.align = "center",
  fig.show = "hold",
  # Etc:
  collapse = TRUE,
  comment = "##"
  # tidy = FALSE
)

library(tidyverse)

# Set output width for rticles:
options(width = 70)
```

# Abstract

The Ada & Archibald MacLeish Field Station is a 250-acre patchwork of forest and pasture land in Whately, MA that presents the opportunity for all members of the Smith College community (students, faculty, staff, and alum) to pursue artistic inquiry, environmental research, outdoor education, and low-impact recreation. The `macleish` R package was created to analyze weather and spatial data based on the MacLeish Field Station.

The package includes the following functionality: multiple layers of map data coded as sf package objects, functions to access historical and live weather readings, data from ongoing forest ecology research, and functions to access photos from a PhenoCam (Phenology Camera) Network video camera mounted on the 25-meter tower records a daily photograph of the forest canopy.

By making this data accessible in an R Package with a simple interface, we hope the `macleish` R package will serve as an educational tool that fosters interdisciplinary collaboration within the Smith College community. At the moment, the package is mostly used in the Statistical & Data Science department, but computational confidence is expected to increase in the Biology department and Environmental Science & Policy program. Accordingly we hope the students in these programs not only use the package but also contribute to it. Furthermore, we view this package as a blueprint for other institutions that possess similar research sites to bring the related research communities together.

# Introduction

Computational analysis is becoming a crucial component of research in ecology. However, programming presents new challenges for ecological investigators who are unfamiliar with statistical applications. Even researchers that are versed in efficient programming may be restricted by knowledge of code. Therefore, interdisciplinary research between ecology and statistics remains limited in scope, depth, and quality (@Visser:2015).

Here, we create an R Package with a simple interface that access to weather, spatial, and photography data to inspire interdisciplinary collaboration. The `macleish` Package, uses data from the Ada and Archibald MacLeish Field Station.

The Ada and Archibald MacLeish Field Station is a 243-acre patchwork of forest and pasture land on top of a flat ridge in Whately, Massachusetts (See Figure \ref{fig:macleish}). The station is located about 11 miles from Smith College. The community at Smith College, including students, faculty, staff, and alum, pursue artistic inquiry, environmental research, outdoor education, and low-impact recreation at the MacLeish Field Station. Students are integral to the operation and maintenance of the field as stewards for the land, designers of programs, and participants in key decision-making (@SmithCollege:2021).

```{r macleish, echo = FALSE, fig.cap="Map of MacLeish Field Station, Whately, Massachusetts, USA.", out.width="50%"}
knitr::include_graphics(path = "macleish.jpg")
```

Although a diverse ecosystem exists in the MacLeish Field Station, invasive insects and fungus have drastically altered the forest composition. American chestnut trees were once the most common tree in New England forests. However, due to the lethal chestnut blight, a fungus from Asia, most chestnut trees died because of infection. To harbor the survival of the American chestnut tree, the tree was crossed with the Chinese chestnut tree, which is resistant to the blight, to create a blight-resistant hybrid. White pine trees were another victim of a fungus native to Asia, referred to as the white pine blister rust. Similar to the chestnut blight, the white pine blister is fatal. Although decades of effort to control the white pine blister rust conserved most of the white pine tree population, a combination of logging and the blister rust greatly reduced the composition of forests at MacLeish. Furthermore, the Eastern Hemlock tree is a martyr of the Hemlock Woolly Adelgid, an invasive insect native to Asia. High volumes of woolly adelgid populations can kill a tree within a few years by weighing down the branches and causing the needles to fall off. Finally, the beech scale insect is an invasive insect from Europe. The insect is capable of carrying the fungus Nectria coccinea, which is transmitted into the tree when the insects feed on beech sap. Nectria coccinea causes the bark of beech trees to blister and crack, making the tree susceptible to further infection by insects and other kinds of fungus. Beech trees infected with the fungus die within six years. Unfortunately, both the Hemlock Woolly adelgid and the beech scale insect are highly resistant to the cold and thrive during the warm. Therefore, trees are threatened by these insects year-round. Similarly, as the climate is projected to warm, the range of both insects will continue to expand (@Moise:2021).

Likewise, other invasive species exist at the MacLeish Field Station. The autumn olive, Japanese barberry, multiflora rose, oriental bittersweet, and wild grape are all invasive species that contend with native Massachusetts plant species. The ability of these invasive species to produce an abundant quantity of seeds, grow quickly, and thrive without natural predators allow them to pose a serious threat to out-compete native species. Conservation research and efforts are ongoing to address the expansion of these invasive species (@Moise:2021).

Within the MacLeish Field Station are a number of stations and administrative buildings that collect data and foster environmental education. For instance, the Whately and Orchard Weather Stations store historical and collect current meteorological weather data. The Smith College Observatory is frequently used by the astronomy department at Smith College for astronomical research. The Bechtel Environmental Classroom was created by the Environmental Science & Policy program using top-notch sustainable strategies. The classroom provides a meeting space for environmental laboratory and educational use (@SmithCollege:2021). Evidently, the MacLeish Field Station is highly interdisciplinary, appealing to multiple departments at once, and aims to inspire research in the arts, humanities, and natural sciences among the Smith College community. Through the `macleish` Package, we hope to expand the opportunity for members of Smith College to pursue research, contribute to the R Package, and influence other institutions with analogous research sites to create more accessible programming interfaces.

Examples of research conducted at MacLeish by Smith Faculty include @Zukswert:2014, @Ignace:2018, @Guswa:2011, @Jackson:2018, @Guswa:2011, @Bassar:2015, @Wetzel:2017, @Visser:2015, and @Moise:2021.

# Statement of Need

The MacLeish Field Station is abundant with scientific inquiry, where the Smith College community explore the diverse ecosystem of plants and animals. The `macleish` package offers access to

1. Data from open-source databases
1. interactive maps of the MacLeish Field Station and surrounding area 
1. Meteorological reading data from historical and current databases 
1. Data on tree diameter of different species infected by the Hemlock Woolly adelgid 
1. A database of images of tree canopy over time

Users may generate usable summary statistics and plots using the data from the `macleish` package.

# `macleish` Package Main Functionalities

To use the `macleish` package, first run `install.packages(macleish)` to install the package in R, then run the following code to load the package:

```{r, message=FALSE, warning=FALSE}
library(macleish)
```

```{r, echo=FALSE, results = FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(forcats)
library(leaflet)
library(dplyr)
library(imager)
library(knitr)
library(qpdf)
```

## Maps of MacLeish

Shapefile-based maps of MacLeish Field Station are available in the `macleish_layers` data object. The following layers will be displayed on the map.

```{r}
names(macleish_layers)
```

Running the following code creates an interactive `leaflet` map for users to zoom in and out, identify the Orchard and Whately Weather Stations, locate the area of MacLeish Field Station, and pinpoint other geographical features such as bodies of water, roads, mountains, trails, and wildlife management areas. Figure \ref{fig:leafletmap} displays a static image of the resulting interactive map.

```{r}
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]], 
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]], 
    weight = 1, popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]], 
    weight = 1, color = "brown",
    popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]], 
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
    popup = ~Label
  )
```

```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
include_graphics(path = "leaflet.png")
```

## Field data

Two tree plot datasets is available through `tree_diameter1` and `tree_diameter2`. The time frame varies between `tree_diameter1` (2010-2015) and `tree_diameter2` (2009-2016), and `tree_diameter2` lacks data on position of individual trees. The datasets present change in tree diameter over a set of years for two plots dominated by the parasites Hemlock Woolly Adelgid. See Tables \ref{tab:tree-diameter-1} and \ref{tab:tree-diameter-2}.

```{r, eval = FALSE}
tree_diameter1
```
```{r tree-diameter-1}
tree_diameter1 %>% 
  head() %>% 
  select(-module) %>% 
  kable(
    format = "latex",
    caption = "Tree diameter dataset 1.",
    booktabs = TRUE,
    escape = FALSE,
    linesep = ""
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  )
```

```{r, eval = FALSE}
tree_diameter2
```
```{r tree-diameter-2}
tree_diameter2 %>% 
  head() %>% 
  select(-module) %>% 
  kable(
    format = "latex",
    caption = "Tree diameter dataset 2.",
    booktabs = TRUE,
    escape = FALSE,
    linesep = ""
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  )
```

For example, using the `tree_diameter1` dataset, the boxplot below demonstrates the distribution of diameter for different species of trees at different positions from 2010-2015.

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot( aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter Between 2010-2015") +
  theme(legend.position="bottom")
```

By viewing an individual species, the distribution of diameter varies based on the position of the species. For instance, the median diameter of emergent Eastern Hemlock trees is the greatest, despite having the smallest overall range. However, the overall range of the diameter of the canopy is the greatest.

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter of Eastern Hemlock tree depending on position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock")) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter for Eastern Hemlock") +
  theme(legend.position="bottom")
```

Below is a box plot of the distribution of diameter based on different tree species from 2009-2012 using the `tree_diameter2` dataset. Using individual data points on top of the box plots reveals the underlying distribution of each group.

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species between 2009-2016."}
tree_diameter2 %>%
  ggplot( aes(x=diameter, y=species)) +
  geom_boxplot() +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", 
       title = "Distribution of Diameter Between 2009-2016") +
  theme(legend.position="bottom")
```

## Weather data

Weather data from 2015 is available through `whately_2015` and `orchard_2015` data objects. Data was recorded every 10 minutes every day from 2015-01-01 to 2015-31-12.

```{r}
whately_2015
```

```{r}
orchard_2015
```

Furthermore, the ETL framework retrieves live and historical (2012-01-03 for Whately and 2014-06-27 for Orchard) weather data from both MacLeish Field Station weather monitors.

## Phenocam functions

The PhenoCam Network is an ecosystem phenology camera network that provides automated, near-surface remote sensing of canopy phenology across the northeastern United States and adjacent Canada, including the MacLeish Field Station. High-resolution digital cameras at the MacLeish Field Station take pictures of the canopy and upload them to the PhenoCam server every half hour. The PhenoCam Network permits analysis of archived images, providing an objective means by which canopy phenology can be monitored and quantified at relatively low cost and with minimal expenses.

Figure \ref{fig:phenocam} displays an example of an image retrieved from the PhenoCam Network.

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
include_graphics("phenocam.jpeg")
```

The function `get_macleish_image()` retrieves an image from the PhenoCam Network when the date and time are specified.

# Application and Perspectives

The `macleish` package is an R Package with a simple interface that access to weather, spatial, and photography data to inspire interdisciplinary collaboration among statisticians and ecologists. This is a dynamic project that was built with the interest of biologists. It currently supports interdisciplinary collaboration to foster statistical application among the ecology community. More functions and data are expected to be compiled in the package over time that seems fit to users to support an increasing collection of statistical analyses and visualizations.

# Acknowledgements

We acknowledge contributions from Jesse Bellemare and Paul Wetzel.

# References

### 2022-06-06 joss_paper/paper.Rmd
moved trail map image

@@
 
+```{r download-trail-map, include=FALSE, eval=FALSE}
+download.file(
+  url = "http://masstrails.com/cache/1007_0.jpg", 
+  destfile = here::here("joss_paper", "macleish_trail_map.jpg")
+)
+```
+
 ```{r macleish, echo = FALSE, fig.cap="Map of MacLeish Field Station, Whately, Massachusetts, USA.", out.width="50%"}
-knitr::include_graphics(path = "macleish.jpg")
+knitr::include_graphics(here::here("joss_paper", "macleish_trail_map.jpg"))
 ```

### 2022-06-06 joss_paper/paper.Rmd
remove unnecessary packages

@@
 
-```{r, echo=FALSE, results = FALSE, warning=FALSE, message=FALSE}
-library(ggplot2)
-library(tidyverse)
-library(hrbrthemes)
-library(viridis)
-library(forcats)
-library(leaflet)
-library(dplyr)
-library(imager)
-library(knitr)
-library(qpdf)
-```
-
 ## Maps of MacLeish
@@
 ```{r}
+library(leaflet)
 map <- leaflet() %>%
@@
 ```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
-include_graphics(path = "leaflet.png")
+knitr::include_graphics(path = "leaflet.png")
 ```
@@
   select(-module) %>% 
-  kable(
+  knitr::kable(
     format = "latex",
@@
 ```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
+library(ggplot2)
 tree_diameter1 %>%
@@
   geom_boxplot() +
-  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
+  scale_fill_viridis_d(alpha=0.6, option="A") +
   scale_x_continuous(limits=c(0,60)) +
@@
   geom_boxplot() +
-  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
+  scale_fill_viridis_d(alpha=0.6, option="A") +
   scale_y_discrete(limits=c("Eastern Hemlock")) +
@@
   geom_jitter(color="black", size=0.4, alpha=0.9) +
-  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
+  scale_fill_viridis_d(alpha=0.6, option="A") +
   scale_x_continuous(limits=c(0,60)) +
@@
 ```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
-include_graphics("phenocam.jpeg")
+knitr::include_graphics("phenocam.jpeg")
 ```

### 2022-06-06 joss_paper/paper.Rmd
ran styler

@@
     data = macleish_layers[["buildings"]],
-    weight = 1, popup = ~ name
+    weight = 1, popup = ~name
   ) %>%
@@
     weight = 1, color = "brown",
-    popup = ~ name
+    popup = ~name
   ) %>%
@@
 tree_diameter1 %>%
-  mutate(position = fct_relevel(position,
+  mutate(position = fct_relevel(
+    position,
     "emergent", "canopy", "subcanopy",
-                                "sapling")) %>%
-  ggplot( aes(x=diameter, y=species, fill=position)) +
+    "sapling"
+  )) %>%
+  ggplot(aes(x = diameter, y = species, fill = position)) +
   geom_boxplot() +
-  scale_fill_viridis_d(alpha=0.6, option="A") +
-  scale_x_continuous(limits=c(0,60)) +
+  scale_fill_viridis_d(alpha = 0.6, option = "A") +
+  scale_x_continuous(limits = c(0, 60)) +
   facet_wrap(~year) +
-  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
-       title = "Distribution of Diameter Between 2010-2015") +
-  theme(legend.position="bottom")
+  labs(
+    x = "Diameter (cm)", y = "Species", fill = "Position",
+    title = "Distribution of Diameter Between 2010-2015"
+  ) +
+  theme(legend.position = "bottom")
 ```
@@
 tree_diameter1 %>%
-  mutate(position = fct_relevel(position,
+  mutate(position = fct_relevel(
+    position,
     "emergent", "canopy", "subcanopy",
-                                "sapling")) %>%
-  ggplot(aes(x=diameter, y=species, fill=position)) +
+    "sapling"
+  )) %>%
+  ggplot(aes(x = diameter, y = species, fill = position)) +
   geom_boxplot() +
-  scale_fill_viridis_d(alpha=0.6, option="A") +
-  scale_y_discrete(limits=c("Eastern Hemlock")) +
-  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
-       title = "Distribution of Diameter for Eastern Hemlock") +
-  theme(legend.position="bottom")
+  scale_fill_viridis_d(alpha = 0.6, option = "A") +
+  scale_y_discrete(limits = c("Eastern Hemlock")) +
+  labs(
+    x = "Diameter (cm)", y = "Species", fill = "Position",
+    title = "Distribution of Diameter for Eastern Hemlock"
+  ) +
+  theme(legend.position = "bottom")
 ```
@@
 tree_diameter2 %>%
-  ggplot( aes(x=diameter, y=species)) +
+  ggplot(aes(x = diameter, y = species)) +
   geom_boxplot() +
-  geom_jitter(color="black", size=0.4, alpha=0.9) +
-  scale_fill_viridis_d(alpha=0.6, option="A") +
-  scale_x_continuous(limits=c(0,60)) +
+  geom_jitter(color = "black", size = 0.4, alpha = 0.9) +
+  scale_fill_viridis_d(alpha = 0.6, option = "A") +
+  scale_x_continuous(limits = c(0, 60)) +
   facet_wrap(~year) +
-  labs(x = "Diameter (cm)", y = "Species", 
-       title = "Distribution of Diameter Between 2009-2016") +
-  theme(legend.position="bottom")
+  labs(
+    x = "Diameter (cm)", y = "Species",
+    title = "Distribution of Diameter Between 2009-2016"
+  ) +
+  theme(legend.position = "bottom")
 ```

### 2022-06-06 joss_paper/paper.Rmd
added map but not working

@@
 
+```{r, eval=FALSE}
+# why doesn't this work?
+map
+```
+
 ```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
@@
 ```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
-knitr::include_graphics("phenocam.jpeg")
+knitr::include_graphics(here::here("joss_paper", "phenocam.jpeg"))
 ```

### 2022-06-07 joss_paper/paper.Rmd
added phenocamr

@@
 
+```{r, eval=FALSE, include=FALSE}
+download.file(phenocam(), here::here("joss_paper", "macleish_latest.jpg"))
+```
+
 ```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
-knitr::include_graphics(here::here("joss_paper", "phenocam.jpeg"))
+knitr::include_graphics(here::here("joss_paper", "macleish_latest.jpg"))
 ```

### 2022-06-07 R/phenocam.R

@@ -1,0 +1,93 @@
+#' Retrieve images from Phenocam
+#' @param when a string to be converted into a date-time
+#' @param ... currently ignored
+#' @export
+#' @examples 
+#' phenocam_image_url()
+#' phenocam_image_url(Sys.time() - 100)
+
+phenocam_image_url <- function(when = NULL, ...) {
+  if (is.null(when)) {
+    url <- "https://phenocam.sr.unh.edu/data/latest/macleish.jpg"
+  } else if (datetime <- as.POSIXct(when)) {
+    url_stem <- "https://phenocam.sr.unh.edu/data/archive/macleish/"
+    url_slug <- format(datetime, "%Y/%m/macleish_%Y_%m_%d_%H%M%S.jpg")
+    url <- paste0(url_stem, url_slug)
+  } else {
+    stop("Could not convert argument to Datetime")
+  }
+  return(url)
+}
+
+#' @rdname phenocam_image_url
+#' @export
+#' @param x a Date
+#' @examples 
+#' \dontrun{
+#' phenocam_read_day_urls()
+#' }
+
+phenocam_read_day_urls <- function(x = Sys.Date()) {
+  the_date <- as.Date(x)
+  url <- paste0(
+    "https://phenocam.sr.unh.edu/webcam/browse/macleish/",
+    format(the_date, "%Y/%m/%d/")
+  )
+  url |>
+    # need authentication to make this work!!
+    xml2::read_html() |>
+    rvest::html_elements("td") |>
+    rvest::html_elements("img") |>
+    rvest::html_attr("src")
+}
+
+
+#' @rdname phenocam_image_url
+#' @export
+#' @examples 
+#' \dontrun{
+#' phenocam_read_month_urls()
+#' }
+
+phenocam_read_month_urls <- function(x = Sys.Date()) {
+  the_date <- as.Date(x)
+  url <- paste0(
+    "https://phenocam.sr.unh.edu/webcam/browse/macleish/",
+    format(the_date, "%Y/%m/")
+  )
+  url |>
+    xml2::read_html() |>
+    rvest::html_elements("td") |>
+    rvest::html_elements("img") |>
+    rvest::html_attr("src") |>
+    stringr::str_subset("macleish")
+}
+
+
+#' MacLeish Phenocam site info
+#' @rdname phenocam_image_url
+#' @export
+#' @examples 
+#' \dontrun{
+#' phenocam_info()
+#' }
+
+phenocam_info <- function() {
[…]

### 2022-06-08 R/phenocam.R
added tests and pass R CMD check

@@ -1,10 +1,15 @@
+globalVariables("site")
+
 #' Retrieve images from Phenocam
+#' @description Phenocam contains over 70,000 images taken from MacLeish.
+#' Photos have been taken every 30 minutes since February 2017.
 #' @param when a string to be converted into a date-time
 #' @param ... currently ignored
 #' @export
+#' @references \url{https://phenocam.sr.unh.edu/webcam/sites/macleish/}
 #' @examples 
 #' phenocam_image_url()
-#' phenocam_image_url(Sys.time() - 100)
+#' phenocam_image_url("2021-12-25 12:05:05")
 
 phenocam_image_url <- function(when = NULL, ...) {
   if (is.null(when)) {

### 2022-06-08 tests/testthat/test-phenocam.R

@@ -1,0 +1,10 @@
+context("test-phenocam")
+
+test_that("Phenocam works", {
+  expect_true(grepl("latest", phenocam_image_url()))
+  
+  skip_on_cran()
+  x <- phenocam_info()
+  expect_equal(nrow(x), 1)
+  expect_equal(x$site, "macleish")
+})

### 2022-06-08 data-raw/spatial.R
set units; close #52

@@ -13,7 +13,6 @@ layers <- c("landmarks", "forests", "streams",
   "boundary", 
   "research", "soil", "trails")
 
-
 macleish_layers <- lapply(layers, st_read, dsn = dsn)
 names(macleish_layers) <- layers
 
@@ -32,11 +31,36 @@ macleish_layers[["forests"]] <- macleish_layers %>%
   purrr::pluck("forests") %>%
   dplyr::rename(type = Sheet1__Na)
 
-# add 30 foot contours
+# add 30-foot contours
 macleish_layers[["elevation"]] <- macleish::mass_gis() %>%
   macleish::macleish_intersect() %>%
   st_transform(4326)
 
+# set units
+macleish_layers[["challenge_courses"]] <- macleish_layers |>
+  purrr::pluck("challenge_courses") %>%
+  mutate(ele = units::set_units(ele, "m"))
+macleish_layers[["wetlands"]] <- macleish_layers |>
+  purrr::pluck("wetlands") %>%
+  mutate(
+    area_acres = units::set_units(AREAACRES, "acre"),
+    area_sqmi = units::set_units(AREAACRES, "mi^2")
+  ) |>
+  select(-contains("AREA", ignore.case = FALSE))
+macleish_layers[["boundary"]] <- macleish_layers |>
+  purrr::pluck("boundary") %>%
+  mutate(
+    area = st_area(geometry),
+    area = units::set_units(area, "acre"),
+  ) |>
+  select(area)
+macleish_layers[["research"]] <- macleish_layers |>
+  purrr::pluck("research") %>%
+  mutate(
+    area = st_area(geometry),
+    area = units::set_units(area, "m^2"),
+  ) |>
+  select(-contains("Shape", ignore.case = FALSE))
 
 # Set coordinate reference system for entire list
 macleish_layers <- lapply(macleish_layers, st_transform, crs = 4326)
@@ -49,7 +73,6 @@ for(i in 1:length(macleish_layers)){
 
 # check to make sure they are all projected the same
 lapply(macleish_layers, st_crs)
-
 
 # Test all layers
 names(macleish_layers)

### 2022-06-08 joss_paper/paper.Rmd
added pkgs.bib

--- 2022-06-06 joss_paper/paper.Rmd
@@
 ---
-title: 'The MacLeish Package: R Package for analyzing weather and spatial data'
+title: 'MacLeish: An R Package for analyzing spatial, temporal, and photographic data for environmental research'
 date: "`r Sys.Date()`"
@@
    index: 1
-bibliography: refs.bib
+bibliography: [pkgs.bib, refs.bib]
 biblio-style: apa
@@
 options(width = 70)
+
+knitr::write_bib(
+  c("etl", "phenocamr"),
+  file = "pkgs.bib"
+)
 ```
 
-# Abstract
+# Summary
 
@@
 Even researchers that are versed in efficient programming may be restricted by knowledge of code.
-Therefore, interdisciplinary research between ecology and statistics remains limited in scope, depth, and quality (@Visser:2015).
+Therefore, interdisciplinary research between ecology and statistics remains limited in scope, depth, and quality [@Visser:2015].
 
@@
 
-The Ada and Archibald MacLeish Field Station is a 243-acre patchwork of forest and pasture land on top of a flat ridge in Whately, Massachusetts (See Figure \ref{fig:macleish}).
+The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is a 243-acre patchwork of forest and pasture land on top of a flat ridge in Whately, Massachusetts (See Figure \ref{fig:macleish}).
 The station is located about 11 miles from Smith College.
 The community at Smith College, including students, faculty, staff, and alum, pursue artistic inquiry, environmental research, outdoor education, and low-impact recreation at the MacLeish Field Station.
-Students are integral to the operation and maintenance of the field as stewards for the land, designers of programs, and participants in key decision-making (@SmithCollege:2021).
+Students are integral to the operation and maintenance of the field as stewards for the land, designers of programs, and participants in key decision-making.
 
@@
 Therefore, trees are threatened by these insects year-round.
-Similarly, as the climate is projected to warm, the range of both insects will continue to expand (@Moise:2021).
+Similarly, as the climate is projected to warm, the range of both insects will continue to expand [@Moise:2021].
 
@@
 The ability of these invasive species to produce an abundant quantity of seeds, grow quickly, and thrive without natural predators allow them to pose a serious threat to out-compete native species.
-Conservation research and efforts are ongoing to address the expansion of these invasive species (@Moise:2021).
+Conservation research and efforts are ongoing to address the expansion of these invasive species [@Moise:2021].
 
@@
 The Bechtel Environmental Classroom was created by the Environmental Science & Policy program using top-notch sustainable strategies.
-The classroom provides a meeting space for environmental laboratory and educational use (@SmithCollege:2021).
-Evidently, the MacLeish Field Station is highly interdisciplinary, appealing to multiple departments at once, and aims to inspire research in the arts, humanities, and natural sciences among the Smith College community.
+The classroom provides a meeting space for environmental laboratory and educational use.
+Evidently, the [MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is highly interdisciplinary, appealing to multiple departments at once, and aims to inspire research in the arts, humanities, and natural sciences among the Smith College community.
 Through the `macleish` Package, we hope to expand the opportunity for members of Smith College to pursue research, contribute to the R Package, and influence other institutions with analogous research sites to create more accessible programming interfaces.
@@
 
-# `macleish` Package Main Functionalities
+# Features
 
@@
 
-## Maps of MacLeish
+## Spatial data
 
@@
 
+```{r, eval=FALSE}
+map
+```
+
 ```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
@@
 
-## Field data
+## Research data
 
@@
 
-Furthermore, the ETL framework retrieves live and historical (2012-01-03 for Whately and 2014-06-27 for Orchard) weather data from both MacLeish Field Station weather monitors.
+Furthermore, the ETL framework [@R-etl; @baumer2019grammar] retrieves live and historical (2012-01-03 for Whately and 2014-06-27 for Orchard) weather data from both MacLeish Field Station weather monitors.
 
-## Phenocam functions
+## Photographic data
 
@@
 The PhenoCam Network permits analysis of archived images, providing an objective means by which canopy phenology can be monitored and quantified at relatively low cost and with minimal expenses.
+[@R-phenocamr]
 
@@
 
-```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
-knitr::include_graphics("phenocam.jpeg")
+```{r, eval=FALSE, include=FALSE}
+download.file(phenocam_image_url(), here::here("joss_paper", "macleish_latest.jpg"))
+download.file(phenocam_image_url("2021-12-25 12:05:05"), here::here("joss_paper", "macleish_xmas.jpg"))
+```
+
+```{r phenocam, echo=FALSE, fig.cap="Images of the MacLeish Field Station retrieved from the PhenoCam Network by the \\texttt{phenocam\\_image\\_url()} function.
+The image on the left was taken in June 2022, while the image on the right was taken in December 2021.
+", fig.show="hold", out.width="49%"}
+knitr::include_graphics(here::here("joss_paper", "macleish_xmas.jpg"))
+knitr::include_graphics(here::here("joss_paper", "macleish_latest.jpg"))
 ```
@@
 
-# Application and Perspectives
+# Conclusion
 

### 2022-06-08 joss_paper/paper.Rmd
full revision

@@
 ---
-title: 'MacLeish: An R Package for analyzing spatial, temporal, and photographic data for environmental research'
+title: 'MacLeish: An R package for monitoring environmental conditions in Whately, Massachusetts'
 date: "`r Sys.Date()`"
@@
     number_sections: yes
+editor_options: 
+  chunk_output_type: console
 ---
@@
 knitr::write_bib(
-  c("etl", "phenocamr"),
+  c("etl", "phenocamr", "sf", "leaflet"),
   file = "pkgs.bib"
@@
 
-The Ada & Archibald MacLeish Field Station is a 250-acre patchwork of forest and pasture land in Whately, MA that presents the opportunity for all members of the Smith College community (students, faculty, staff, and alum) to pursue artistic inquiry, environmental research, outdoor education, and low-impact recreation.
-The `macleish` R package was created to analyze weather and spatial data based on the MacLeish Field Station.
+The Ada & Archibald MacLeish Field Station is a parcel of land in Whately, MA owned and operated by Smith College. 
+The `macleish` R package provides spatial, meteorological, and photographic data for monitoring environmental conditions at the site. 
+Numerous faculty use the MacLeish Field Station for research purposes.
 
-The package includes the following functionality: multiple layers of map data coded as sf package objects, functions to access historical and live weather readings, data from ongoing forest ecology research, and functions to access photos from a PhenoCam (Phenology Camera) Network video camera mounted on the 25-meter tower records a daily photograph of the forest canopy.
+The `macleish` package includes multiple layers of spatial data, functions to access historical and live weather readings, data from ongoing forest ecology research, and functions to access photographs taken by a PhenoCam (Phenology Camera) Network digital camera mounted on the 25-meter WhatelyMet tower.
+The camera captures a photograph of the forest canopy every 30 minutes.
 
-By making this data accessible in an R Package with a simple interface, we hope the `macleish` R package will serve as an educational tool that fosters interdisciplinary collaboration within the Smith College community.
-At the moment, the package is mostly used in the Statistical & Data Science department, but computational confidence is expected to increase in the Biology department and Environmental Science & Policy program.
-Accordingly we hope the students in these programs not only use the package but also contribute to it.
-Furthermore, we view this package as a blueprint for other institutions that possess similar research sites to bring the related research communities together.
+By making these data accessible in an R package with a simple interface, we hope the `macleish` R package will foster interdisciplinary collaboration within the Smith College community.
 
-# Introduction
+# About the MacLeish Field Station
 
-Computational analysis is becoming a crucial component of research in ecology.
-However, programming presents new challenges for ecological investigators who are unfamiliar with statistical applications.
-Even researchers that are versed in efficient programming may be restricted by knowledge of code.
-Therefore, interdisciplinary research between ecology and statistics remains limited in scope, depth, and quality [@Visser:2015].
+From the [Smith College website]([Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)):
 
-Here, we create an R Package with a simple interface that access to weather, spatial, and photography data to inspire interdisciplinary collaboration.
-The `macleish` Package, uses data from the Ada and Archibald MacLeish Field Station.
-
-The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is a 243-acre patchwork of forest and pasture land on top of a flat ridge in Whately, Massachusetts (See Figure \ref{fig:macleish}).
-The station is located about 11 miles from Smith College.
-The community at Smith College, including students, faculty, staff, and alum, pursue artistic inquiry, environmental research, outdoor education, and low-impact recreation at the MacLeish Field Station.
-Students are integral to the operation and maintenance of the field as stewards for the land, designers of programs, and participants in key decision-making.
+> The Ada and Archibald MacLeish Field Station, a uniquely liberal arts field station, is a 250-acre patchwork of forest and pasture land in nearby Whately that provides opportunities for all members of the Smith community (students, faculty, staff, and alum) to pursue artistic inquiry, environmental research, outdoor education and low-impact recreation.
+Students are integral to the field station: they help steward the land, design programs for their peers and participate in making key decisions in the operation of the field station.
+The Bechtel Environmental classroom provides meeting and dry laboratory space for MacLeish users.
 
@@
 ```
-
-Although a diverse ecosystem exists in the MacLeish Field Station, invasive insects and fungus have drastically altered the forest composition.
-American chestnut trees were once the most common tree in New England forests.
-However, due to the lethal chestnut blight, a fungus from Asia, most chestnut trees died because of infection.
-To harbor the survival of the American chestnut tree, the tree was crossed with the Chinese chestnut tree, which is resistant to the blight, to create a blight-resistant hybrid.
-White pine trees were another victim of a fungus native to Asia, referred to as the white pine blister rust.
-Similar to the chestnut blight, the white pine blister is fatal.
-Although decades of effort to control the white pine blister rust conserved most of the white pine tree population, a combination of logging and the blister rust greatly reduced the composition of forests at MacLeish.
-Furthermore, the Eastern Hemlock tree is a martyr of the Hemlock Woolly Adelgid, an invasive insect native to Asia.
-High volumes of woolly adelgid populations can kill a tree within a few years by weighing down the branches and causing the needles to fall off.
-Finally, the beech scale insect is an invasive insect from Europe.
-The insect is capable of carrying the fungus Nectria coccinea, which is transmitted into the tree when the insects feed on beech sap.
-Nectria coccinea causes the bark of beech trees to blister and crack, making the tree susceptible to further infection by insects and other kinds of fungus.
-Beech trees infected with the fungus die within six years.
-Unfortunately, both the Hemlock Woolly adelgid and the beech scale insect are highly resistant to the cold and thrive during the warm.
-Therefore, trees are threatened by these insects year-round.
-Similarly, as the climate is projected to warm, the range of both insects will continue to expand [@Moise:2021].
-
-Likewise, other invasive species exist at the MacLeish Field Station.
-The autumn olive, Japanese barberry, multiflora rose, oriental bittersweet, and wild grape are all invasive species that contend with native Massachusetts plant species.
-The ability of these invasive species to produce an abundant quantity of seeds, grow quickly, and thrive without natural predators allow them to pose a serious threat to out-compete native species.
-Conservation research and efforts are ongoing to address the expansion of these invasive species [@Moise:2021].
-
-Within the MacLeish Field Station are a number of stations and administrative buildings that collect data and foster environmental education.
-For instance, the Whately and Orchard Weather Stations store historical and collect current meteorological weather data.
-The Smith College Observatory is frequently used by the astronomy department at Smith College for astronomical research.
-The Bechtel Environmental Classroom was created by the Environmental Science & Policy program using top-notch sustainable strategies.
-The classroom provides a meeting space for environmental laboratory and educational use.
-Evidently, the [MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is highly interdisciplinary, appealing to multiple departments at once, and aims to inspire research in the arts, humanities, and natural sciences among the Smith College community.
-Through the `macleish` Package, we hope to expand the opportunity for members of Smith College to pursue research, contribute to the R Package, and influence other institutions with analogous research sites to create more accessible programming interfaces.
-
-Examples of research conducted at MacLeish by Smith Faculty include @Zukswert:2014, @Ignace:2018, @Guswa:2011, @Jackson:2018, @Guswa:2011, @Bassar:2015, @Wetzel:2017, @Visser:2015, and @Moise:2021.
+Figure \ref{fig:macleish} shows a trail map illustrating the MacLeish property.
+@Moise:2021 provides an interactive history of the property. 
+Research by Smith faculty and students conducted at MacLeish includes 
+@guswa2012effect, 
+@guswa2012canopy,
+@zukswert2014forest, 
+@visser2015speeding, 
+@bassar2016changes, 
+@Wetzel:2017,
+@ignace2018decline, 
+@jackson2018potential.
 
@@
 
-To use the `macleish` package, first run `install.packages(macleish)` to install the package in R, then run the following code to load the package:
+To use the CRAN version of the `macleish` package, first run `install.packages(macleish)` to install the package, then load it:
 
@@
 
-Shapefile-based maps of MacLeish Field Station are available in the `macleish_layers` data object. The following layers will be displayed on the map.
+Spatial data from the MacLeish Field Station are available through the `macleish_layers` data object, which leverages the `sf` package [@R-sf]. 
+The following layers are available:
 
@@
 
-Running the following code creates an interactive `leaflet` map for users to zoom in and out, identify the Orchard and Whately Weather Stations, locate the area of MacLeish Field Station, and pinpoint other geographical features such as bodies of water, roads, mountains, trails, and wildlife management areas.
+Any `sf` objects can be placed on an interactive map created by the `leaflet` package [@R-leaflet].
+Figure \ref{fig:leafletmap} situates the MacLeish property in Whately, to the east of the Northampton Reservoir and to the west of the Mt.
+Esther Wildlife Management Area, pinpoints the OrchardMet and WhatelyMet weather stations, and depicts other geographical features such as streams and trails.
 Figure \ref{fig:leafletmap} displays a static image of the resulting interactive map.
@@
 library(leaflet)
-map <- leaflet() %>%
-  addTiles() %>%
+map <- leaflet() |>
+  addTiles() |>
   addPolygons(
@@
     weight = 1, fillOpacity = 0.1
-  ) %>%
+  ) |>
   addPolygons(
@@
     weight = 1, popup = ~name
-  ) %>%
+  ) |>
   addPolylines(
@@
     popup = ~name
-  ) %>%
+  ) |>
   addPolylines(
@@
     weight = 2
-  ) %>%
+  ) |>
   addMarkers(
@@
     popup = ~Label
-  )
+  ) |>
+  setView(-72.67918, 42.44921, zoom = 14)
 ```
@@
 
-```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
+```{r leafletmap, echo=FALSE, fig.cap="Screenshot from an interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
 knitr::include_graphics(path = "leaflet.png")
@@
 
-Two tree plot datasets is available through `tree_diameter1` and `tree_diameter2`.
-The time frame varies between `tree_diameter1` (2010-2015) and `tree_diameter2` (2009-2016), and `tree_diameter2` lacks data on position of individual trees.
+Two tree plot datasets are available: `tree_diameter1` and `tree_diameter2`. 
+The time frame differs between `tree_diameter1` (2010--2015) and `tree_diameter2` (2009--2016), and `tree_diameter2` lacks data on position of individual trees. 
 The datasets present change in tree diameter over a set of years for two plots dominated by the parasites Hemlock Woolly Adelgid.
-See Tables \ref{tab:tree-diameter-1} and \ref{tab:tree-diameter-2}.
+Tables \ref{tab:tree-diameter-1} and \ref{tab:tree-diameter-2} show samples from these datasets.
 
@@
 ```
-```{r tree-diameter-1}
-tree_diameter1 %>%
-  head() %>%
-  select(-module) %>%
+```{r tree-diameter-1, echo=FALSE}
+tree_diameter1 |>
+  head() |>
+  select(-module) |>
   knitr::kable(
     format = "latex",
-    caption = "Tree diameter dataset 1.",
+    caption = "Sample of the first six rows of the first tree diameter dataset. \\label{tab:tree1}",
     booktabs = TRUE,
@@
     linesep = ""
-  ) %>%
+  ) |>
   kableExtra::kable_styling(
@@
 ```
-```{r tree-diameter-2}
-tree_diameter2 %>%
-  head() %>%
-  select(-module) %>%
+```{r tree-diameter-2, echo=FALSE}
+tree_diameter2 |>
+  head() |>
+  select(-module) |>
   knitr::kable(
     format = "latex",
-    caption = "Tree diameter dataset 2.",
+    caption = "Sample of the first six rows of the second tree diameter dataset. \\label{tab:tree2}",
     booktabs = TRUE,
@@
 
-For example, using the `tree_diameter1` dataset, the boxplot below demonstrates the distribution of diameter for different species of trees at different positions from 2010-2015.
+For example, using the `tree_diameter1` dataset, the boxplot in Figure \ref{fig:tree-diam} demonstrates the distribution of diameter for different species of trees at different positions from 2010--2015.
 
-```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
+```{r tree-diam, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010--2015."}
 library(ggplot2)
-tree_diameter1 %>%
+tree_diameter1 |>
   mutate(position = fct_relevel(
@@
     "sapling"
-  )) %>%
+  )) |>
   ggplot(aes(x = diameter, y = species, fill = position)) +
@@
 
-```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter of Eastern Hemlock tree depending on position between 2010-2015."}
-tree_diameter1 %>%
-  mutate(position = fct_relevel(
-    position,
-    "emergent", "canopy", "subcanopy",
-    "sapling"
-  )) %>%
-  ggplot(aes(x = diameter, y = species, fill = position)) +
-  geom_boxplot() +
-  scale_fill_viridis_d(alpha = 0.6, option = "A") +
-  scale_y_discrete(limits = c("Eastern Hemlock")) +
-  labs(
-    x = "Diameter (cm)", y = "Species", fill = "Position",
-    title = "Distribution of Diameter for Eastern Hemlock"
-  ) +
-  theme(legend.position = "bottom")
+## Weather data
+
+Weather data from 2015 is available through the `whately_2015` and `orchard_2015` data objects. 
+These data were recorded every 10 minutes every day from 2015-01-01 to 2015-31-12, and include measurements like temperature, wind speed, and relative humidity.
+
+```{r}
+head(whately_2015)
 ```
 
-Below is a box plot of the distribution of diameter based on different tree species from 2009-2012 using the `tree_diameter2` dataset. 
-Using individual data points on top of the box plots reveals the underlying distribution of each group.
-
-```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species between 2009-2016."}
-tree_diameter2 %>%
-  ggplot(aes(x = diameter, y = species)) +
-  geom_boxplot() +
-  geom_jitter(color = "black", size = 0.4, alpha = 0.9) +
-  scale_fill_viridis_d(alpha = 0.6, option = "A") +
-  scale_x_continuous(limits = c(0, 60)) +
-  facet_wrap(~year) +
-  labs(
-    x = "Diameter (cm)", y = "Species",
-    title = "Distribution of Diameter Between 2009-2016"
-  ) +
-  theme(legend.position = "bottom")
-```
-
-## Weather data
-
-Weather data from 2015 is available through `whately_2015` and `orchard_2015` data objects. Data was recorded every 10 minutes every day from 2015-01-01 to 2015-31-12.
-
-```{r}
-whately_2015
-```
-
-```{r}
-orchard_2015
-```
-
-Furthermore, the ETL framework [@R-etl; @baumer2019grammar] retrieves live and historical (2012-01-03 for Whately and 2014-06-27 for Orchard) weather data from both MacLeish Field Station weather monitors.
+Furthermore, live and historical (to present from 2012-01-03 for WhatelyMet and from 2014-06-27 for OrchardMet) weather data from both MacLeish Field Station weather monitors is available for download through functionality provided by the `etl` package [@R-etl; @baumer2019grammar].
 
@@
 
-The PhenoCam Network is an ecosystem phenology camera network that provides automated, near-surface remote sensing of canopy phenology across the northeastern United States and adjacent Canada, including the MacLeish Field Station.
-High-resolution digital cameras at the MacLeish Field Station take pictures of the canopy and upload them to the PhenoCam server every half hour.
+The PhenoCam Network is an ecosystem phenology camera network that provides automated, near-surface remote sensing of canopy phenology across the northeastern United States and Canada. 
+One such high-resolution digital camera sits atop the WhatelyMet tower, takes pictures of the canopy every 30 minutes, and then uploads them to the PhenoCam server. 
 The PhenoCam Network permits analysis of archived images, providing an objective means by which canopy phenology can be monitored and quantified at relatively low cost and with minimal expenses.
-[@R-phenocamr]
 
-Figure \ref{fig:phenocam} displays an example of an image retrieved from the PhenoCam Network.
+Figure \ref{fig:phenocam} displays two examples of images retrieved from the PhenoCam Network by the `phenocam_image_url()` function, which leverages functionality provided by the `phenocamr` package [@R-phenocamr].
 
@@
 
-The function `get_macleish_image()` retrieves an image from the PhenoCam Network when the date and time are specified.
-
 # Conclusion
 
-The `macleish` package is an R Package with a simple interface that access to weather, spatial, and photography data to inspire interdisciplinary collaboration among statisticians and ecologists.
-This is a dynamic project that was built with the interest of biologists.
-It currently supports interdisciplinary collaboration to foster statistical application among the ecology community.
-More functions and data are expected to be compiled in the package over time that seems fit to users to support an increasing collection of statistical analyses and visualizations.
+The `macleish` package for R has a simple interface that accesses to weather, meteorological, and photographic data to inspire interdisciplinary collaboration among statisticians and ecologists.
 
@@
 
-We acknowledge contributions from Jesse Bellemare and Paul Wetzel.
+We acknowledge contributions from Jesse Bellemare, Paul Wetzel, Reid Bertone-Johnson, and Jon Caris.
 

### 2022-06-09 joss_paper/paper.Rmd

@@
 @Moise:2021 provides an interactive history of the property.
-Research by Smith faculty and students conducted at MacLeish includes 
+
+# Statement of Need
+
+The MacLeish Field Station is rife with scientific inquiry, as the Smith College community explores the diverse ecosystem of plants and animals. 
+While numerous research papers, including 
 @guswa2012effect, 
@@
 @ignace2018decline, 
-@jackson2018potential.
+@jackson2018potential
+make use of the MacLeish property, the data supporting these research efforts is not centralized or easily accessible to the public.
+The `macleish` package offers easy, public access to:
 
-# Statement of Need
+1. spatial data on building, landmarks, streams, trails, and other features of the MacLeish Field Station property 
+1. real-time and historical meteorological measurements
+1. carefully collected data on tree diameters of different species infected by the Hemlock Woolly adelgid 
+1. photographic images of the tree canopy over time
 
-The MacLeish Field Station is abundant with scientific inquiry, where the Smith College community explore the diverse ecosystem of plants and animals. The `macleish` package offers access to
-
-1. Data from open-source databases
-1. interactive maps of the MacLeish Field Station and surrounding area 
-1. Meteorological reading data from historical and current databases 
-1. Data on tree diameter of different species infected by the Hemlock Woolly adelgid 
-1. A database of images of tree canopy over time
-
-Users may generate usable summary statistics and plots using the data from the `macleish` package.
+These data are already used in data science textbooks [@baumer2021mdsr] and new research efforts in progress.
 
@@
 
-# Conclusion
-
-The `macleish` package for R has a simple interface that accesses to weather, meteorological, and photographic data to inspire interdisciplinary collaboration among statisticians and ecologists.
-
 # Acknowledgements

### 2022-06-29 joss_paper/paper.Rmd

@@
 
-By making these data accessible in an R package with a simple interface, we hope the `macleish` R package will foster interdisciplinary collaboration within the Smith College community.
+By delivering data from a variety of sources in a common, easy-to-use interface, the `macleish` package fosters interdisciplinary collaborations within environmental research communities.
 
@@
 
-The MacLeish Field Station is rife with scientific inquiry, as the Smith College community explores the diverse ecosystem of plants and animals. 
-While numerous research papers, including 
+The MacLeish Field Station enables scientific inquiry, as the Smith College community explores the diverse ecosystem of plants and animals. 
+While numerous research projects (see 
 @guswa2012effect, 
@@
 @jackson2018potential
-make use of the MacLeish property, the data supporting these research efforts is not centralized or easily accessible to the public.
+for examples)
+make use of the MacLeish property, the data supporting these efforts is not centralized or easily accessible to the public.
 The `macleish` package offers easy, public access to:
@@
 1. real-time and historical meteorological measurements
-1. carefully collected data on tree diameters of different species infected by the Hemlock Woolly adelgid 
+1. carefully collected data on tree diameters of different species infected by the [Hemlock Woolly adelgid](https://en.wikipedia.org/wiki/Hemlock_woolly_adelgid) 
 1. photographic images of the tree canopy over time
@@
 Any `sf` objects can be placed on an interactive map created by the `leaflet` package [@R-leaflet].
-Figure \ref{fig:leafletmap} situates the MacLeish property in Whately, to the east of the Northampton Reservoir and to the west of the Mt.
+Figure \ref{fig:leafletmap} situates the MacLeish property in [Whately](https://en.wikipedia.org/wiki/Whately,_Massachusetts), to the east of the Northampton Reservoir and to the west of the Mt.
 Esther Wildlife Management Area, pinpoints the OrchardMet and WhatelyMet weather stations, and depicts other geographical features such as streams and trails.
@@
 The time frame differs between `tree_diameter1` (2010--2015) and `tree_diameter2` (2009--2016), and `tree_diameter2` lacks data on position of individual trees. 
-The datasets present change in tree diameter over a set of years for two plots dominated by the parasites Hemlock Woolly Adelgid.
+The datasets present change in tree diameter over a set of years for two plots dominated by the parasitic Hemlock Woolly Adelgid.
 Tables \ref{tab:tree-diameter-1} and \ref{tab:tree-diameter-2} show samples from these datasets.
@@
 
-For example, using the `tree_diameter1` dataset, the boxplot in Figure \ref{fig:tree-diam} demonstrates the distribution of diameter for different species of trees at different positions from 2010--2015.
+The boxplot in Figure \ref{fig:tree-diam} uses the `tree_diameter1` data set to demonstrate the distribution of diameter for different species of trees at different positions from 2010--2015.
 
@@
 By viewing an individual species, the distribution of diameter varies based on the position of the species. 
-For instance, the median diameter of emergent Eastern Hemlock trees is the greatest, despite having the smallest overall range.
+For instance, the median diameter of emergent [Eastern Hemlock](https://en.wikipedia.org/wiki/Tsuga_canadensis) trees is the greatest, despite having the smallest overall range. 
 However, the overall range of the diameter of the canopy is the greatest.
@@
 
-The PhenoCam Network is an ecosystem phenology camera network that provides automated, near-surface remote sensing of canopy phenology across the northeastern United States and Canada. 
+The [PhenoCam Network](https://phenocam.nau.edu/webcam/) is an ecosystem phenology camera network that provides automated, near-surface remote sensing of canopy phenology across the northeastern United States and Canada.
 One such high-resolution digital camera sits atop the WhatelyMet tower, takes pictures of the canopy every 30 minutes, and then uploads them to the PhenoCam server. 
@@
 
-We acknowledge contributions from Jesse Bellemare, Paul Wetzel, Reid Bertone-Johnson, and Jon Caris.
+We acknowledge a variety of contributions from Jesse Bellemare, Paul Wetzel, Reid Bertone-Johnson, Jon Caris, Rose Goueth, Wencong Li, Weijia Zhang, and Nicholas Horton.
 

### 2022-06-29 R/phenocam.R
added midday image url function

@@ -51,10 +51,10 @@ phenocam_read_day_urls <- function(x = Sys.Date()) {
 #' @export
 #' @examples 
 #' \dontrun{
-#' phenocam_read_month_urls()
+#' phenocam_read_monthly_midday_urls()
 #' }
 
-phenocam_read_month_urls <- function(x = Sys.Date()) {
+phenocam_read_monthly_midday_urls <- function(x = Sys.Date()) {
   the_date <- as.Date(x)
   url <- paste0(
     "https://phenocam.sr.unh.edu/webcam/browse/macleish/",
@@ -68,6 +68,22 @@ phenocam_read_month_urls <- function(x = Sys.Date()) {
     stringr::str_subset("macleish")
 }
 
+#' @rdname phenocam_image_url
+#' @export
+#' @examples 
+#' \dontrun{
+#' phenocam_image_url_midday(Sys.Date() - 3)
+#' phenocam_image_url_midday(Sys.Date() - 365)
+#' }
+
+phenocam_image_url_midday <- function(x = Sys.Date()) {
+  monthlies <- phenocam_read_monthly_midday_urls(x)
+  this_day <- format(as.Date(x), "%Y_%m_%d")
+  
+  monthlies |>
+    stringr::str_subset(this_day) |>
+    head(1)
+}
 
 #' MacLeish Phenocam site info
 #' @rdname phenocam_image_url

### 2022-06-29 R/phenocam.R
updated URLs

@@ -6,16 +6,16 @@ globalVariables("site")
 #' @param when a string to be converted into a date-time
 #' @param ... currently ignored
 #' @export
-#' @references \url{https://phenocam.sr.unh.edu/webcam/sites/macleish/}
+#' @references \url{https://phenocam.nau.edu/webcam/sites/macleish/}
 #' @examples 
 #' phenocam_image_url()
 #' phenocam_image_url("2021-12-25 12:05:05")
 
 phenocam_image_url <- function(when = NULL, ...) {
   if (is.null(when)) {
-    url <- "https://phenocam.sr.unh.edu/data/latest/macleish.jpg"
+    url <- "https://phenocam.nau.edu/data/latest/macleish.jpg"
   } else if (datetime <- as.POSIXct(when)) {
-    url_stem <- "https://phenocam.sr.unh.edu/data/archive/macleish/"
+    url_stem <- "https://phenocam.nau.edu/data/archive/macleish/"
     url_slug <- format(datetime, "%Y/%m/macleish_%Y_%m_%d_%H%M%S.jpg")
     url <- paste0(url_stem, url_slug)
   } else {
@@ -35,7 +35,7 @@ phenocam_image_url <- function(when = NULL, ...) {
 phenocam_read_day_urls <- function(x = Sys.Date()) {
   the_date <- as.Date(x)
   url <- paste0(
-    "https://phenocam.sr.unh.edu/webcam/browse/macleish/",
+    "https://phenocam.nau.edu/webcam/browse/macleish/",
     format(the_date, "%Y/%m/%d/")
   )
   url |>
@@ -57,7 +57,7 @@ phenocam_read_day_urls <- function(x = Sys.Date()) {
 phenocam_read_monthly_midday_urls <- function(x = Sys.Date()) {
   the_date <- as.Date(x)
   url <- paste0(
-    "https://phenocam.sr.unh.edu/webcam/browse/macleish/",
+    "https://phenocam.nau.edu/webcam/browse/macleish/",
     format(the_date, "%Y/%m/")
   )
   url |>

### 2022-07-14 joss_paper/paper.Rmd
booktabs

@@
   chunk_output_type: console
+header-includes:
+  - \usepackage{booktabs}
 ---

### 2025-11-21 README.Rmd
Phenocam on README
upgrade pipe

@@
 macleish <- etl("macleish")
-macleish %>%
+macleish |>
   etl_update()
@@
 ```{r, eval=FALSE}
-whately <- macleish %>%
+whately <- macleish |>
   tbl("whately")
-whately %>%
-  mutate(the_year = strftime('%Y', when)) %>%
-  group_by(the_year) %>%
+whately |>
+  mutate(the_year = strftime('%Y', when)) |>
+  group_by(the_year) |>
   summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
 
-orchard <- macleish %>%
+orchard <- macleish |>
   tbl("orchard")
-orchard %>%
-  mutate(the_year = strftime('%Y', when)) %>%
-  group_by(the_year) %>%
+orchard |>
+  mutate(the_year = strftime('%Y', when)) |>
+  group_by(the_year) |>
   summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(temperature))
@@
 ```{r, eval=FALSE, fig.width = 7, fig.height = 5, message=FALSE}
-daily <- whately %>%
-  mutate(the_date = date(when)) %>%
-  group_by(the_date) %>%
-  summarize(N = n(), avgTemp = mean(temperature)) %>%
+daily <- whately |>
+  mutate(the_date = date(when)) |>
+  group_by(the_date) |>
+  summarize(N = n(), avgTemp = mean(temperature)) |>
   collect()
@@
 library(leaflet)
-leaflet() %>%
-  addTiles() %>%
+leaflet() |>
+  addTiles() |>
   addPolygons(
@@
     weight = 1, popup = ~ name
-  ) %>%
+  ) |>
   addPolylines(
@@
     popup = ~ name
-  ) %>%
+  ) |>
   addPolylines(
@@
 
+## Images
+
+You can download live and historical images from Phenocam.
+
+```{r}
+phenocam_image_url()
+```
+
+```{r figures-side, fig.show="hold", out.width="50%"}
+knitr::include_graphics(phenocam_image_url())
+knitr::include_graphics(phenocam_image_url("2021-12-25 12:05:05"))
+```
+
 ## See also

### 2025-11-21 R/data.R

@@ -61,8 +61,8 @@
 #' \dontrun{
 #' #' # loose wire anomalies
 #' if (require(dplyr) & require(ggplot2) & require(lubridate)) {
-#'  orchard_2015 %>%
-#'  filter(month(when) == 11) %>%
+#'  orchard_2015 |>
+#'  filter(month(when) == 11) |>
 #'    ggplot(aes(x = when, y = temperature)) +
 #'    geom_line() + geom_smooth()
 #' }

### 2025-11-21 R/etl_extract.R

@@ -10,42 +10,42 @@
 #' str(macleish)
 #' 
 #' \dontrun{
-#' macleish %>%
-#'   etl_extract() %>%
-#'   etl_transform() %>%
+#' macleish |>
+#'   etl_extract() |>
+#'   etl_transform() |>
 #'   etl_load()
-#' whately <- macleish %>%
+#' whately <- macleish |>
 #'   tbl("whately") 
-#' orchard <- macleish %>%
+#' orchard <- macleish |>
 #'   tbl("orchard") 
 #'   
-#' whately %>%
+#' whately |>
 #'   summarize(N = n(), avg_temp = mean(temperature))
-#' orchard %>%
+#' orchard |>
 #'   summarize(N = n(), avg_temp = mean(temperature))
 #'   
 #' # check data types
-#' whately %>%
+#' whately |>
 #'   glimpse()
 #' 
 #' # if using SQLite, datetimes will get converted to integers
-#' whately <- whately %>%
+#' whately <- whately |>
 #'   mutate(when_datetime = datetime(when, 'unixepoch'))
-#' whately %>%
+#' whately |>
 #'   glimpse()
 #' 
 #' # show the most recent data -- should be within the past hour
-#' whately %>%
-#'   collect() %>%
+#' whately |>
+#'   collect() |>
 #'   tail()
 #' 
 #' # show that no time-shifting is happening
 #' if (require(ggplot2)) {
-#' macleish %>%
-#'   tbl("whately") %>%
-#'   collect() %>%
-#'   mutate(when = lubridate::ymd_hms(when)) %>%
-#'   filter(lubridate::year(when) == 2012 & month(when) == 12 & day(when) == 20) %>%
+#' macleish |>
+#'   tbl("whately") |>
+#'   collect() |>
+#'   mutate(when = lubridate::ymd_hms(when)) |>
+#'   filter(lubridate::year(when) == 2012 & month(when) == 12 & day(when) == 20) |>
 #'   ggplot(aes(x = when, y = temperature)) + geom_line()
 #' }
 #' }
@@ -86,30 +86,30 @@ etl_transform_help <- function(obj, ...) {
   x <- readr::read_csv(lcl, skip = 1)
[…]

### 2025-11-21 R/mass_gis.R

@@ -32,7 +32,7 @@ mass_gis <- function(layer = "contours250k") {
   lcl_shp <- file.path(dir, layer)
   utils::unzip(lcl_zip, exdir = lcl_shp)
   # list.files(dir)
-  sf::st_read(lcl_shp) %>%
+  sf::st_read(lcl_shp) |>
     sf::st_transform(4326)
 }
 

### 2025-11-21 R/phenocam.R

@@ -38,11 +38,11 @@ phenocam_read_day_urls <- function(x = Sys.Date()) {
     "https://phenocam.nau.edu/webcam/browse/macleish/",
     format(the_date, "%Y/%m/%d/")
   )
-  url %>%
+  url |>
     # need authentication to make this work!!
-    xml2::read_html() %>%
-    rvest::html_elements("td") %>%
-    rvest::html_elements("img") %>%
+    xml2::read_html() |>
+    rvest::html_elements("td") |>
+    rvest::html_elements("img") |>
     rvest::html_attr("src")
 }
 
@@ -60,11 +60,11 @@ phenocam_read_monthly_midday_urls <- function(x = Sys.Date()) {
     "https://phenocam.nau.edu/webcam/browse/macleish/",
     format(the_date, "%Y/%m/")
   )
-  url %>%
-    xml2::read_html() %>%
-    rvest::html_elements("td") %>%
-    rvest::html_elements("img") %>%
-    rvest::html_attr("src") %>%
+  url |>
+    xml2::read_html() |>
+    rvest::html_elements("td") |>
+    rvest::html_elements("img") |>
+    rvest::html_attr("src") |>
     stringr::str_subset("macleish")
 }
 
@@ -80,8 +80,8 @@ phenocam_image_url_midday <- function(x = Sys.Date()) {
   monthlies <- phenocam_read_monthly_midday_urls(x)
   this_day <- format(as.Date(x), "%Y_%m_%d")
   
-  monthlies %>%
-    stringr::str_subset(this_day) %>%
+  monthlies |>
+    stringr::str_subset(this_day) |>
     head(1)
 }
 
@@ -94,7 +94,7 @@ phenocam_image_url_midday <- function(x = Sys.Date()) {
 #' }
 
 phenocam_info <- function() {
-  phenocamr::list_sites() %>%
+  phenocamr::list_sites() |>
     dplyr::filter(site == "macleish")
 }
 

### 2025-11-21 tests/testthat/test-macleish.R

@@ -11,8 +11,8 @@ test_that("data integrity", {
   
   # # For some reason this test fails only on Oracle Solaris 10, x86, 32 bit, R-release
   # # via devtools::check_rhub(env_vars=c(R_COMPILE_AND_INSTALL_PACKAGES = "always"), platforms = "solaris-x86-patched")
-  # epsg <- macleish_layers %>%
-  #   purrr::map(sf::st_crs) %>%
+  # epsg <- macleish_layers |>
+  #   purrr::map(sf::st_crs) |>
   #   purrr::map_int(`$`, "epsg")
   # expect_true(all(epsg == 4326))
   

### 2025-11-21 README.Rmd
updated URL

@@
 
-The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
+The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/discover-smith/smith-action/sustainable-smith/macleish-field-station) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.
 
@@
 
-- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
+- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/discover-smith/smith-action/sustainable-smith/macleish-field-station)
 - **[etl](https://github.com/beanumber/etl)**

### 2025-11-21 joss_paper/paper.Rmd
updated URL

@@
 
-From the [Smith College website]([Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)):
+From the [Smith College website]([Ada and Archibald MacLeish Field Station](https://www.smith.edu/discover-smith/smith-action/sustainable-smith/macleish-field-station)):
 

### 2025-11-21 R/data.R

@@ -52,7 +52,7 @@
 #'   \item{par_density}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average density of Watts/meters^2. One of two solar measurements for Orchard}
 #'   \item{par_total}{Photosynthetically Active Radiation (sunlight between 400 and 700 nm), in average total over measurement period of Watts/meters^2. One of two solar measurements for Orchard}
 #' }
-#' @source These data are recorded at <https://www.smith.edu/about-smith/sustainable-smith/ceeds> 
+#' @source These data are recorded at <https://www.smith.edu/discover-smith/smith-action/sustainable-smith/center-environment-ecological-design-sustainability> 
 "whately_2015"
 
 #' @rdname whately_2015
